---
title: "2-data_cleaning_and_descriptive"
author: ""
date: "2024-12-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# set directory
```{r}
setwd("your_directory")
file_path="your_directory"
```

# input- output
```{r}
input="output_1_after_quality_check.csv"
output= "output_2_after_quality_check.csv"
```

# libraries
```{r}
library(esc)
library(dplyr) 
library(purrr)  # For map functions
library(ggplot2)
library(gridExtra)
library(tidyverse) # needed for 'glimpse'
library(meta)
library(metafor)
library(dmetar)
library(robumeta)
library(clubSandwich)
library(rmarkdown)
library(metaviz)
library(gghalves)  #for geom_half_boxplot
library(tidyr)
library(readr)
library(sf)
library(viridis)
library(knitr)
library(kableExtra)
library(modelsummary)
```

# plot theme
```{r}
library(ggplot2)

# Define a color-blind friendly palette
color_blind_friendly_palette <- c(
  "#B1B424",  # Olive Yellow (new, to bridge between yellow and green)
  "#4C92C3",  # Azure (new, slightly darker than sky blue)
  "#8673A1",  # Lavender Indigo (new, to bridge between blue and purple)
  "#8FBC8F",  # Dark Sea Green
  "#009E73",  # Bluish Green
  "#56B4E9",  # Sky Blue
  "#0072B2",  # Blue
  "#6C8EBF",  # Soft Blue
  "#5E81AC",  # Queen Blue (new, a darker soft blue)
  "#483D8B",  # Dark Slate Blue
  "#CC79A7",  # Reddish Purple
  "#CC6677",  # Soft Red
  "#DECBE4",  # Pale Purple
  "#D1B2A5",  # Sand
  "#A89984",  # Taupe (new, to bridge between sand and grey)
  "#999933",  # Olive Green
  "#BDB76B",  # Dark Khaki
  "#8B4513",  # Saddle Brown
  "#949494",  # Grey
  "#777777",  # Medium Grey (new, to smooth transition to darker greys)
  "#525252",  # Dark Grey
  "#893F45"
)

# Define the plot theme 
plot_theme <- theme_minimal(base_size = 14) +  # Slightly larger base font size for better readability
  theme(
    plot.title = element_text(face = "bold", size = 16, color = "black"),  # Black for clarity and emphasis
    plot.subtitle = element_text(face = "plain", size = 14, color = "grey70"),  # Subtitle in a lighter grey for hierarchy
    legend.title = element_text(face = "bold", color = "black"),  # Black for consistency with titles
    legend.text = element_text(size = 12),
    axis.title = element_text(face = "bold", size = 14, color = "black"),  # Black for main axis titles
    axis.text = element_text(color = "black"),  # Black for axis text for maximum readability
    panel.grid.major.x = element_blank(),  # Remove major grid lines along x
    panel.grid.major.y = element_blank(),  # Remove major grid lines along y
    panel.grid.minor.x = element_blank(),  # Remove minor grid lines along x
    panel.grid.minor.y = element_blank(),  # Remove minor grid lines along y
    axis.line = element_line(color = "black"),  # Add black line for x and y axes
    legend.position = "bottom",  # Legend at the bottom to not overlap with data visualization
    legend.background = element_rect(fill = "white", color = NA),  # White background for legend for clarity
    legend.box.background = element_rect(color = "grey80"),  # Light grey border for legend
    legend.box.margin = margin(5, 5, 5, 5)
  )

# Apply the theme to a sample plot
sample_plot <- ggplot(mpg, aes(x = displ, y = hwy, color = class)) +
  geom_point(alpha = 0.6) +
  scale_color_manual(values = color_blind_friendly_palette) +
  labs(
    title = "Engine Displacement vs. Highway Miles Per Gallon",
    subtitle = "Data from the 'mpg' dataset",
    x = "Engine Displacement (L)",
    y = "Miles Per Gallon (Highway)",
    color = "Vehicle Class"
  ) +
  plot_theme

# Print the plot
#print(sample_plot)


```

#0-  Parameters
```{r}
# correlation between within-study effects
rho=0.8
threshold_for_moderator=2
```

```{r}
adjust_stars <- function(sig) {
  # Reduces each level by one star
  # Assumes sig can be "*", "**", "***"; modifies to "", "*", "**"
  ifelse(sig == "***", "**", 
         ifelse(sig == "**", "*", 
                ifelse(sig == "*", "", sig)))
}
```


# 1- Data Cleaning & Preparation
```{r}
# 1- Read the data from the CSV file
ma_feedback_time_data <- read_csv(input)

# 2- Replace "no_info" and "NA " values with NA
ma_feedback_time_data[ma_feedback_time_data == "no_info"] <- NA
ma_feedback_time_data[ma_feedback_time_data == "NA"] <- NA

# first define experiment number
ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(experiment_number = paste0("Experiment ", expt_num))

# 3- Convert necessary columns to numeric
numeric_columns <- c('year', 'expt_num', 'feedback_delay_difference', 'mean_age', 'sd_age', 'min_age', 'max_age', 'gender', 'n_excluded', 'retention_interwal.day._i', 'retention_interwal.day._d', 'nb_times_feedback_provided_i', 'nb_times_feedback_provided_d', 'nb_question.item_in_training', 
'N_total', 'n_i', 'n_d', 'mean_i', 'mean_d', 'sd_i', 'sd_d', 'se_i', 'se_d',
'lower_CI', 'upper_CI', 't', 'SEM', 'F', 'F_sign_change', 'p', 'eta_square',
'partial_eta_square', 'odd_ratio', 'log_odd', 'SE_log_odd', 'corr', 'power', 'beta',
'SE_beta', 'n_point', 'effect_size_original', 'SE_original', 'effect_size_by_calculator', 
'se_by_calculator', 'effect_size', 'standard_error', 'effect_size_alternative', 
'standard_error_alternative', 'n', 'hedges_g', 'se_g','retention_interval_difference_last_feedback_posttest_immediate_vs_delayed', 'feedback_delay_difference_converted_to_time.sec.','delay_i.seconds.item.','delay_d.seconds.item.')

# Convert columns to numeric, safely and checking for existence
ma_feedback_time_data[numeric_columns] <- lapply(numeric_columns, function(col) {
  if (col %in% names(ma_feedback_time_data)) {
    # Safely convert to numeric
    safe_conversion <- suppressWarnings(as.numeric(as.character(ma_feedback_time_data[[col]])))
    if (any(is.na(safe_conversion) & !is.na(ma_feedback_time_data[[col]]))) {
      warning(paste("NA introduced by coercion in column:", col))
    }
    return(safe_conversion)
  } else {
    warning(paste("Warning: Column", shQuote(col), "not found in the DataFrame."))
    return(ma_feedback_time_data[[col]]) # Return the original column if it exists
  }
})

# 4- Log transformations where applicable

ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(feedback_delay_difference_converted = feedback_delay_difference_converted_to_time.sec.)
         
         
ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(feedback_delay_difference = if_else(delay_definition == "second", log(feedback_delay_difference), feedback_delay_difference),
         retention_interval_difference_last_feedback_posttest_immediate_vs_delayed = log(retention_interval_difference_last_feedback_posttest_immediate_vs_delayed+ 0.0001),
         feedback_delay_difference_converted_to_time.sec. = log(feedback_delay_difference_converted_to_time.sec.))

# 5- Recode values in a categorical column
ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(experimental_vs_curriculum_based_task = recode(experimental_vs_curriculum_based_task,
                                                        "experimental_task" = "experimental",
                                                        "curriculum_based_tasl" = "curriculum_based"))
# 6- Create new columns based on conditions
ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(
    retention_interval = ifelse(retention_interwal.day._i == retention_interwal.day._d, 
                                retention_interwal.day._i, 
                                NA),  # Use generic NA which adapts to numeric context
    
    feedback_provided = ifelse(feedback_provided_i == feedback_provided_d, 
                               feedback_provided_i, 
                               NA_character_),  # Explicitly use NA_character_ if these are character columns
    
    feedback_i_d_rate = ifelse(!is.na(nb_times_feedback_provided_i) & !is.na(nb_times_feedback_provided_d), 
                               nb_times_feedback_provided_i / nb_times_feedback_provided_d, 
                               NA),  # Use generic NA which adapts to numeric context
    
    feedback_remind_answer = ifelse(feedback_remind_answer_i == feedback_remind_answer_d, 
                                    feedback_remind_answer_i, 
                                    NA_character_)  # Explicitly use NA_character_ if these are character columns
  )

# 7- Define and apply classification functions
classify_feedback_type <- function(feedback) {
  if (startsWith(feedback, "mixed")) {
    if (grepl("verification", feedback)) {
      return("mixed_include_verification")
    } else {
      return("mixed_not_include_verification")
    }
  } else {
    return(feedback)
  }
}

classify_feedback_type_kr_kcr_ef_tryagain <- function(feedback) {
  if (grepl("mixed\\(verification\\+correct_response\\+elaborated\\)", feedback)) {
    return("elaborated")
  } else if (grepl("mixed\\(verification\\+elaborated\\)", feedback)) {
    return("elaborated")
  } else if (grepl("mixed\\(correct_response\\+elaborated\\)", feedback)) {
    return("elaborated")
  } else if (grepl("mixed\\(verification\\+try_again\\)", feedback)) {
    return("try_again")
  } else if (grepl("mixed\\(verification\\+correct_response\\)", feedback)) {
    return("correct_response")
  } else {
    return(feedback)
  }
}


# Define the classify_feedback_type_simple_elaborated function
classify_feedback_type_simple_elaborated <- function(feedback) {
  if (grepl("mixed\\(verification\\+correct_response\\+elaborated\\)", feedback)) {
    return("elaborated")
  } else if (grepl("mixed\\(verification\\+elaborated\\)", feedback)) {
    return("elaborated")
  } else if (grepl("mixed\\(correct_response\\+elaborated\\)", feedback)) {
    return("elaborated")
  } else if (grepl("mixed\\(verification\\+correct_response\\)", feedback)) {
    return("simple")
  } else if (grepl("\\bverification\\b", feedback)) {
    return("simple")
  } else if (grepl("\\bcorrect_response\\b", feedback)) {
    return("simple")
  } else if (grepl("mixed\\(verification\\+try_again\\)", feedback)) {
    return("simple")
  } else {
    return(feedback)
  }
}


# Apply the function to create the new column
ma_feedback_time_data$feedback_type_mixed_grouped <- sapply(ma_feedback_time_data$feedback_type, classify_feedback_type)
ma_feedback_time_data$feedback_type_kr_kcr_ef_tryagain <- sapply(ma_feedback_time_data$feedback_type, classify_feedback_type_kr_kcr_ef_tryagain)
ma_feedback_time_data$feedback_type_simple_elaborated <- sapply(ma_feedback_time_data$feedback_type, classify_feedback_type_simple_elaborated)

# add variance
ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(
    vi_g = se_g^2,  # Create 'vi' as the square of 'se_g'
    g_ID = as.character(paste("es", seq_len(nrow(ma_feedback_time_data)), sep = "_"))  # Ensure 'es_ID' is character
  )

ma_feedback_time_data <- ma_feedback_time_data %>%
  group_by(unique_ID, expt_num) %>%
  mutate(unique_sample_ID = cur_group_id()) %>%
  ungroup() 

# add new education_level (all others that are not "tertiary" categorized as "other")
# ma_feedback_time_data <- ma_feedback_time_data %>%
#   mutate(
#     educational_level_tertiary_others = if_else(educational_level == "tertiary", "tertiary", "other")
#   )

# ma_feedback_time_data <- ma_feedback_time_data %>%
#   mutate(
#     educational_level_tertiary_others = case_when(
#       educational_level %in% c("tertiary", "adult_education") ~ "tertiary+adult",
#       educational_level %in% c("primary", "secondary") ~ "primary+secondary",
#       TRUE ~ "other"  # This will categorize all remaining levels as "other"
#     )
#   )

# 8- Create and save the analysis data frame
necessary_columns <- c('unique_ID', 'g_ID', 'unique_sample_ID','expt_num', 'effect_size', 'standard_error', 'n', 'hedges_g', 'se_g', 'vi_g')
moderator_columns <- c('country_data_collected_from','publication_type','mean_age', 'gender','feedback_type', 'feedback_type_mixed_grouped', 'delay_definition','feedback_delay_difference','delay_i.seconds.item.','delay_d.seconds.item.','educational_level','learning_domain', 
                    'task_level', 'experimental_vs_curriculum_based_task','participant_design', 'arbitrary_learning','item_posttest', 
                    'delayed_feedback_given_in', 'retention_interval', 'feedback_provided', 'feedback_remind_answer', 'nb_question.item_in_training', 
                    'posttest_category', 'learning_material_type_in_training','memory_retrieval_vs_knowledge_application', 
                    'feedback_type_kr_kcr_ef_tryagain', 'feedback_type_simple_elaborated','year','time_limit_for_answer', 'time_limit_for_answer_include_not_reported',
                    'feedback_i_d_rate','interval_btw_last_feedback_and_posttest_controlled', 'prior_knowledge','feedback_delay_difference_converted_to_time.sec.', 'retention_interval_difference_last_feedback_posttest_immediate_vs_delayed','experiment_number','feedback_delay_difference_converted')


# 9- Recode values in a categorical column to eliminate typos etc
ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(arbitrary_learning = recode(arbitrary_learning,
                                                        "yes" = "arbitrary",
                                                        "no" = "non_arbitrary"))

ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(feedback_remind_answer = recode(feedback_remind_answer,
                                                        "yes" = "remind",
                                                        "no" = "not_remind"))

ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(time_limit_for_answer = recode(time_limit_for_answer,
                                                        "yes" = "answer_time_limited",
                                                        "no" = "answer_time_not_limited"))


# time limit including not reported
ma_feedback_time_data <- ma_feedback_time_data %>%
  mutate(time_limit_for_answer_include_not_reported = if_else(
    is.na(time_limit_for_answer_not_indicated_explicitly) | time_limit_for_answer_not_indicated_explicitly != "yes",
    time_limit_for_answer,
    NA_character_  # Use the appropriate NA type
  ))

 ma_feedback_time_data <- ma_feedback_time_data %>%
   mutate(time_limit_for_answer_include_not_reported = replace_na(time_limit_for_answer_include_not_reported, "not_reported"))
 
 
ma_feedback_time_data_analysis <- ma_feedback_time_data %>%
  select(all_of(c(necessary_columns, moderator_columns))) %>%
  rename(se_effect_size = standard_error, sample_size = n, nb_item_in_training = nb_question.item_in_training, 
         retention_interval_difference_btw_lastfeedback_posttest = retention_interval_difference_last_feedback_posttest_immediate_vs_delayed,
         feedback_delay_difference_converted_to_time_log = feedback_delay_difference_converted_to_time.sec.)


## some cleaning re-coding for moderator analysis
ma_feedback_time_data_analysis <- ma_feedback_time_data_analysis %>%
  mutate(task_level = recode(task_level, "mixed" = "higher_order"))

ma_feedback_time_data_analysis <- ma_feedback_time_data_analysis %>%
  mutate(memory_retrieval_vs_knowledge_application = recode(memory_retrieval_vs_knowledge_application, "mixed" = "knowledge_application"))





# 11- Save to new CSV file
write_csv(ma_feedback_time_data_analysis, output)

# 12- Print the first 5 rows of the new DataFrame
print(head(ma_feedback_time_data_analysis))
```

# 2- Descriptive

## 2.1- Country- World Map

### Map Function

```{r}
# Mapping of country names from your dataset to the shapefile names
name_mapping <- c(
  "US" = "United States of America",
  "UK" = "United Kingdom",
  "Saudi_Arabia" = "Saudi Arabia"
)

# Applying the mapping to your data
ma_feedback_time_data_analysis <- ma_feedback_time_data_analysis %>%
  mutate(
    country_data_collected_from = ifelse(
      country_data_collected_from %in% names(name_mapping),
      name_mapping[country_data_collected_from],
      country_data_collected_from
    )
  )

# Function for world map plots
plot_map <- function(fill, data = ma_feedback_time_data_analysis){
  # Download "Admin 0 – Countries" from
  # https://www.naturalearthdata.com/downloads/110m-cultural-vectors/
  world_map <- read_sf("ne_110m_admin_0_countries/ne_110m_admin_0_countries.shp") %>% 
    # remove Antarctica
    filter(ISO_A3 != "ATA")
  
  # make summary data to plot on map
  participants_by_country = data %>% 
    group_by(country_data_collected_from, unique_sample_ID) %>% 
    summarise(participants_per_sample = max(sample_size)) %>% 
    group_by(country_data_collected_from) %>% 
    summarize(participants = sum(participants_per_sample)) %>% 
    # uneven numbers may occur where we didn't have information on how many 
    # participants in treatment vs. control group and assumed an even split 
    # (i.e. dividing overal n by number of condition)
    mutate_if(is.numeric, round, digits = 0)
  
  map_data <- data %>% 
    group_by(country_data_collected_from) %>% 
    summarise(papers = n_distinct(unique_ID), 
              samples = n_distinct(unique_sample_ID),
              effects = n_distinct(g_ID), 
              yi = mean(hedges_g)
    ) %>% 
    left_join(participants_by_country) %>% 
    # make cutoff versions that allow for better plotting
    mutate(papers_cut = case_when(papers == 1 ~ "1", 
                                  papers <= 5 ~ "2-5", 
                                  papers <= 10 ~ "5-10", 
                                  papers > 10 ~ as.character(max(papers))), 
           papers_cut = fct_relevel(as.factor(papers_cut), "1", "2-5","5-10", as.character(max(papers))),
           samples_cut = case_when(samples == 1 ~ "1", 
                                   samples <= 5 ~ "2-5", 
                                   samples <= 10 ~ "5-10", 
                                   samples > 10 ~ as.character(max(samples))), 
           samples_cut = fct_relevel(as.factor(samples_cut), "1", "2-5","5-10", as.character(max(samples))),
           effects_cut = case_when(effects == 1 ~ "1", 
                                   effects <= 5 ~ "2-5", 
                                   effects <= 10 ~ "5-10", 
                                   effects <= 15 ~ "10-15",
                                   effects > 15 ~ ">15"), 
           effects_cut = fct_relevel(as.factor(effects_cut), "1", "2-5","5-10", "10-15",">15"),
           participants_cut = case_when(participants < 500 ~ "< 500", 
                                        participants < 1000 ~ "500 - 1'000",  
                                        participants < 2000 ~ "1'000 - 2'000",
                                        participants < 5000 ~ "2'000 - 5'000",
                                        participants < 10000 ~ "5'000 - 10'000",
                                        participants < 15000 ~ "10'000 - 15'000",
                                        participants > 15000 ~ as.character(max(participants))),
           participants_cut = fct_relevel(as.factor(participants_cut), "< 500", 
                                          "500 - 1'000","1'000 - 2'000", "2'000 - 5'000", 
                                          "5'000 - 10'000", "10'000 - 15'000", 
                                          as.character(max(participants))),
           participants_num = ifelse(participants <=5000, participants, 5001)
    )
  
  # combine geo data and summarized data
  map <- left_join(world_map, map_data, by = c("ADMIN" = "country_data_collected_from"))
  
  if (fill == "papers") {
    # papers
    papers <- ggplot() + 
      geom_sf(data = map, 
              aes(fill = papers_cut),
              size = 0.25) +
      coord_sf(crs = st_crs("ESRI:54030")) +  # Robinson
      scale_fill_viridis_d(option = "plasma", begin = 0.2, end = 0.9) +
      labs(fill = "Papers") +
      plot_theme +
      theme_void() +
      theme(legend.position = "bottom")
    return(papers)
  }
  
  if (fill == "samples") {
    # samples
    samples <- ggplot() + 
      geom_sf(data = map, 
              aes(fill = samples_cut),
              size = 0.25, 
              alpha = 0.6) +
      coord_sf(crs = st_crs("ESRI:54030")) +  # Robinson
      scale_fill_viridis_d(option = "plasma", begin = 0.8, end = 1, direction = -1) +
      labs(fill = "Samples") +
      plot_theme +
      theme_void() +
      theme(legend.position = "bottom") 
    return(samples)
  }
  
  
  if (fill == "participants") {
    
    # Define the number of colors in the scale
    n_colors <- 20000
    
    # Generate the color scale
    palette <- colorRampPalette(c("#FCFDBFCC", "black"), interpolate = "linear")(n_colors)
    
    # # alternative from viridis
    # palette <- viridis(n_colors, 
    #                    alpha = 0.8, begin = 0, end = 1, direction = -1, option = "rocket")
    
    # assign (more or less) proportional color
    colors <- c(palette[1], palette[1000], palette[2000], palette[3500], palette[7500], palette[12500], palette[length(palette)])
    
    
    participants <- ggplot() + 
      geom_sf(data = map , 
              aes(fill = participants_cut),
              size = 0.25) +
      coord_sf(crs = st_crs("ESRI:54030")) +  # Robinson
      scale_fill_manual(values = colors, 
                        na.value = "white") +
      labs(fill = "Participants") +
      theme_void() +
      theme(legend.position = "bottom")
    return(participants)
  }
  
  if(fill == "effects") {
    
    # Define the number of colors in the scale
    n_colors <- 15
    
    # generate color scale
    palette <- viridis(n_colors,
                       alpha = 0.8, begin = 0.65, end = 1, direction = -1, option = "rocket")
    
    # # Manual Alternative 
    # # Define the start and end points for the color scale
    # start_color <- "#FFFFE5"  # Very light yellow
    # end_color <- "#FFD700"    # Dark yellow, almost orange
    # 
    # # Generate the color scale
    # palette <- colorRampPalette(c(start_color, end_color), interpolate = "linear")(n_colors)
    
    # assign (more or less) proportional color
    colors <- c(palette[1], palette[5], palette[12], palette[15], "black")
    
    
    effects <- ggplot() + 
      geom_sf(data = map , 
              aes(fill = effects_cut),
              size = 0.25) +
      coord_sf(crs = st_crs("ESRI:54030")) +  # Robinson
      scale_fill_manual(values = colors, 
                        na.value = "white", 
                        guide = guide_legend(nrow = 1)) +
      labs(fill = "Effect sizes") +
      theme_void() +
      theme(legend.position = "bottom",
            legend.text = element_text(size = 10),  # Adjust the text size
            legend.key.height = unit(0.5, "lines"),  # Set the height of the legend keys
            legend.box.spacing = unit(0.1, "lines")  # Adjust the spacing between the legend keys
            )
    return(effects)
  }
}

```

Run map funciton
!! need ne_110m_admin_0_countries to be downloaded from: https://www.naturalearthdata.com/downloads/110m-cultural-vectors/

```{r}
effects_map_plot <- plot_map(fill = "papers", data = ma_feedback_time_data_analysis)

effects_map_plot

# Save the plot to a file
ggsave("effects_map_plot.png", plot = effects_map_plot, width = 10, height = 8, dpi = 300)

```

## 2.2- Distributions

```{r}

plot_distribution <- function(data, variable, variable_type, grouping_value) {
  
  # Define a named vector for mapping
  grouping_columns <- c(
      papers = "unique_ID",
      effects = "g_ID",
      samples = "unique_sample_ID"
  )
  
  # Retrieve the appropriate column name using the grouping_value parameter
  if (!grouping_value %in% names(grouping_columns)) {
      stop("Invalid grouping_value. Use 'papers', 'effects', or 'samples'.")
  }
  grouping_column <- grouping_columns[[grouping_value]]
  
  # Prepare the data: summarize it based on the variable type
  data_summary <- data %>%
    group_by_at(vars(one_of(grouping_column))) %>%
    summarise(
      value = if(variable_type == "continuous") {
        max(get(variable), na.rm = TRUE)
      } else {
        if(n_distinct(get(variable)) == 1) {
          first(get(variable))  # If only one unique value, use it
        } else {
          warning(paste("Multiple unique values found in", deparse(substitute(data)), "for group", cur_group_id(), "- cannot summarize uniquely."))
          NA_character_  # Use NA to indicate non-unique categorical data
        }
      },
      .groups = 'drop'
    )

  # plot
 
  # Count NA values
  #na_count <- sum(is.na(data[[variable]]))
 na_counts <- data %>%
    group_by_at(vars(one_of(grouping_column))) %>%
    summarise(na_count = sum(is.na(get(variable))), .groups = 'drop')
 na_count <-nrow(subset(na_counts, na_count != 0))
 
 
 
  # Further processing for categorical data to count occurrences of each value
  if(variable_type == "categorical") {
    value_counts <- data_summary %>%
      group_by(value) %>%
      summarise(count = n(), .groups = 'drop')
    
    # Determine the number of unique categories
    num_categories <- n_distinct(value_counts$value)
    
  # Choose the palette based on the number of categories
  palette <- if(num_categories > 20) {
    viridis(num_categories, option = "D")  # using viridis for many categories
  } else {
    color_blind_friendly_palette  # predefined palette for fewer categories
  }

    # Generate bar plot for categorical data
    plot <- ggplot(value_counts, aes(x = value, y = count, fill = value)) +
      geom_bar(stat = "identity", position = "dodge") +
      geom_text(aes(label = count), vjust = -0.3, size = 3.5) +
      scale_fill_manual(values = palette) +
      labs(x = gsub("_", " ", variable), y = "Count", title = "") +
      #labs(x = gsub("_", " ", variable), y = "Count", title = paste("Distribution of", variable, "grouped by", grouping_value)) +
      scale_x_discrete(labels = function(x) gsub("_", " ", x)) +
      coord_flip() +
      plot_theme +
      theme(legend.position = "none")
  } else if(variable_type == "continuous") {
    
    
    # Compute statistics
        stats <- data_summary %>%
      summarise(
        mean = mean(as.numeric(value[!is.infinite(value) & !is.na(value)])),
        sd = sd(as.numeric(value[!is.infinite(value) & !is.na(value)])),
        se = sd / sqrt(n()),
        lower_ci = mean - qt(0.975, df = n() - 1) * se,
        upper_ci = mean + qt(0.975, df = n() - 1) * se,
        max = max(as.numeric(value[!is.infinite(value) & !is.na(value)])), min = min(as.numeric(value[!is.infinite(value) & !is.na(value)])),
        .groups = 'drop',
      )

    # Continuous data: Use a scatter plot with a density line and error bars for confidence intervals
        
    plot <- ggplot(data_summary, aes(x = value)) +
      geom_histogram(bins = 100, fill = "#0072B2", color = "black", alpha = 0.5) +
      geom_vline(xintercept = stats$mean, color = "#CC79A7", linetype = "dashed", size = 1) +
      geom_point(data = stats, aes(x = mean, y = 0), color = "#CC79A7", size = 4) +
      #geom_errorbar(data = stats, aes(x = mean, ymin = lower_ci, ymax = upper_ci), width = 0.2, color = "#CC79A7") +
      geom_density(aes(y = ..scaled..), fill = NA, color = "#0072B2", alpha = 0.7) +
      geom_label(x = Inf, y = Inf, label = paste("Mean:", round(stats$mean, 2) ,"\nSD:", round(stats$sd, 2), "\nMax:", round(stats$max,2), "\nMin:", round(stats$min,2), "\nNb NA:", na_count), hjust = 1.1, vjust = 1.1, size = 3, fill = "white") +
      labs(x = gsub("_", " ", variable), y = "Density/Frequency", title = paste("Distribution of", variable, "grouped by", grouping_value, "\nNA values:", na_count)) +
      plot_theme
  } else {
    stop("Invalid variable_type. Use 'categorical' or 'continuous'.")
  }

  return(plot)
}

```

### Descriptives

```{r}

# country
plot_descriptive_country_data_collected_from=plot_distribution(data = ma_feedback_time_data_analysis, variable = "country_data_collected_from", variable_type = "categorical", grouping_value = "effects")
plot_descriptive_country_data_collected_from
ggsave("plot_descriptive_country_data_collected_from.png", plot = plot_descriptive_country_data_collected_from, width = 8, height = 6, dpi = 300)

plot_descriptive_country_data_collected_from=plot_distribution(data = ma_feedback_time_data_analysis, variable = "country_data_collected_from", variable_type = "categorical", grouping_value = "papers")
plot_descriptive_country_data_collected_from
ggsave("plot_descriptive_country_data_collected_from.png", plot = plot_descriptive_country_data_collected_from, width = 8, height = 6, dpi = 300)

# nb effect size per paper
plot_descriptive_nb_effect_size=plot_distribution(data = ma_feedback_time_data_analysis, variable = "unique_ID", variable_type = "categorical", grouping_value = "effects")
plot_descriptive_nb_effect_size
ggsave("plot_descriptive_nb_effect_size.png", plot = plot_descriptive_nb_effect_size, width = 8, height = 6, dpi = 300)

analysis_results <- ma_feedback_time_data_analysis %>%
  group_by(unique_ID) %>%
  summarise(n_effect_per_paper = n(), .groups = 'drop')

# Step 2: Calculate mean, minimum, mode, and maximum of the counts
summary_stats <- analysis_results %>%
  summarise(
    Mean = mean(n_effect_per_paper),
    Min = min(n_effect_per_paper),
    Max = max(n_effect_per_paper),
    Mode = as.numeric(names(which.max(table(n_effect_per_paper))))  # Mode calculation
  )

# Print the summary statistics
print(summary_stats)

# cumulative sample size:
grouped_sample_size <- ma_feedback_time_data_analysis %>%
  group_by(unique_ID) %>%
  summarise(total_sample_size = sum(sample_size), .groups = 'drop')

cumulative_sample_size <- sum(grouped_sample_size$total_sample_size)
cat("Cumulative sample size from all papers is", cumulative_sample_size)


# sample size distribution per papers
plot_descriptive_sample_size=plot_distribution(data = ma_feedback_time_data_analysis, variable = "sample_size", variable_type = "continuous", grouping_value = "papers")
plot_descriptive_sample_size
ggsave("plot_descriptive_sample_size.png", plot = plot_descriptive_sample_size, width = 8, height = 6, dpi = 300)

# gender distribution per papers
plot_descriptive_gender=plot_distribution(data = ma_feedback_time_data_analysis, variable = "gender", variable_type = "continuous", grouping_value = "papers")
plot_descriptive_gender
ggsave("plot_descriptive_gender.png", plot = plot_descriptive_gender, width = 8, height = 6, dpi = 300)

# mean age distribution per papers
plot_descriptive_mean_age=plot_distribution(data = ma_feedback_time_data_analysis, variable = "mean_age", variable_type = "continuous", grouping_value = "papers")
plot_descriptive_mean_age
ggsave("plot_descriptive_mean_age.png", plot = plot_descriptive_mean_age, width = 8, height = 6, dpi = 300)


# publication year distribution per papers
plot_descriptive_year=plot_distribution(data = ma_feedback_time_data_analysis, variable = "year", variable_type = "continuous", grouping_value = "papers")
plot_descriptive_year
ggsave("plot_descriptive_year.png", plot = plot_descriptive_year, width = 8, height = 6, dpi = 300)


# publication type distribution per papers
plot_descriptive_publication_type=plot_distribution(data = ma_feedback_time_data_analysis, variable = "publication_type", variable_type = "categorical", grouping_value = "papers")
plot_descriptive_publication_type
ggsave("plot_descriptive_publication_type.png", plot = plot_descriptive_publication_type, width = 8, height = 6, dpi = 300)


# publication type distribution per papers
plot_descriptive_publication_type=plot_distribution(data = ma_feedback_time_data_analysis, variable = "publication_type", variable_type = "categorical", grouping_value = "effects")
plot_descriptive_publication_type
ggsave("plot_descriptive_publication_type.png", plot = plot_descriptive_publication_type, width = 8, height = 6, dpi = 300)


#plot_distribution(data = ma_feedback_time_data_analysis, variable = "learning_domain", variable_type = "categorical", grouping_value = "effects")

# hedges g distribution
plot_descriptive_nb_effect_size=plot_distribution(data = ma_feedback_time_data_analysis, variable = "hedges_g", variable_type = "continuous", grouping_value = "papers")
plot_descriptive_nb_effect_size
ggsave("plot_descriptive_nb_effect_size.png", plot = plot_descriptive_nb_effect_size, width = 8, height = 6, dpi = 300)
```


# 3- Pooling the Effect Sizes 
```{r}
g_feedback_time_corr  <-  robu(formula = hedges_g ~ 1, data = ma_feedback_time_data_analysis,
                            studynum = unique_ID, var.eff.size = vi_g,
                            rho = rho,  modelweights = "CORR", small = FALSE)
print(g_feedback_time_corr)

# sensitivity analysis for different rho
sensitivity(g_feedback_time_corr)


# Extract for Latex
# Extract reg_table from your model
reg_table <- g_feedback_time_corr$reg_table

# Number of effect sizes (k)
k <- nrow(g_feedback_time_corr$data.full)

# Main description for the subset
subset_description <- "Immediate vs. delayed feedback"

# Assuming reg_table is derived from your 'robu' model
# We'll place each value in its corresponding column now
results_table <- tibble(
  Statistic = c(
    "Immediate vs. delayed feedback", 
    "Num. Obs.", "N", "rho", "I^2", "tau^2"
  ),
  Estimate = c(
    as.character(round(g_feedback_time_corr$reg_table$b.r, 2)),  # g value
    as.character(nrow(g_feedback_time_corr$data.full)),  # Num. Obs.
    as.character(length(unique(g_feedback_time_corr$data.full$study))),  # N
    as.character(g_feedback_time_corr$mod_info$rho),  # rho
    as.character(format(g_feedback_time_corr$mod_info$I.2, digits = 2)),  # I^2
    as.character(format(g_feedback_time_corr$mod_info$tau.sq, digits = 4))  # tau^2
  ),
  `Std. Error` = c(
    as.character(round(g_feedback_time_corr$reg_table$SE, 2)),  # SE value
    "", "", "", "", ""  # Empty for additional stats
  ),
  `t Statistic` = c(
    as.character(round(g_feedback_time_corr$reg_table$t, 2)),  # t value
    "", "", "", "", ""  # Empty for additional stats
  ),
  `P value` = c(
    format.pval(g_feedback_time_corr$reg_table$prob, digits = 3, eps = 0.001, na.form = "<.001"),  # P-value
    "", "", "", "", ""  # Empty for additional stats
  ),
  `95% CI` = c(
    paste0("[", round(g_feedback_time_corr$reg_table$CI.L, 2), ", ", round(g_feedback_time_corr$reg_table$CI.U, 2), "]"),  # 95% CI
    "", "", "", "", ""  # Empty for additional stats
  ),
  `Sig` = c(
    g_feedback_time_corr$reg_table$sig,  # Significance
    "", "", "", "", ""  # Empty for additional stats
  )
)

# Create the LaTeX table using kableExtra
latex_table <- results_table %>%
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "lllllll",  # Alignment for each column
    col.names = c("Statistic", "Estimate", "Std. Error", "t Statistic", "P value", "95% CI", "Sig")
  ) %>%
  kable_styling(
    latex_options = c("hold_position"),
    full_width = FALSE
  ) %>%
  add_header_above(c(" " = 1, "Robust Variance Estimates Model" = 6)) %>%
  row_spec(
    0,  # Insert a horizontal line after the description of the subset
    extra_latex_after = "\\midrule"
  )

# Write the LaTeX table to a .tex file
tex_filename <- normalizePath(file.path(file_path, "model_with_outlier.tex"), mustWork = FALSE)
tryCatch({
  cat(latex_table, file = tex_filename)
  if (file.exists(tex_filename)) {
    message("File successfully created: ", tex_filename)
  } else {
    warning("Failed to create file: ", tex_filename)
  }
}, error = function(e) {
  warning("An error occurred while writing file: ", e$message)
})

# Print the LaTeX table
cat(latex_table)

```

# 4- Outliers 

From preregistration
 
We will check the adjusted effect sizes (Hedges' g) for potential outliers by assessing whether any effect sizes deviate by more than three standard deviations from the group mean effect sizes. This step ensures that no single study disproportionately influences the summary statistics or introduces bias into our analysis. This method is adapted from Van der Kleij et al. (2015) in their study on feedback effects in computer-based learning environments.

## 4.a - Outliers Detection
```{r}
# Calculate the mean and standard deviation of Hedges' g
mean_hedges_g <- mean(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE)
sd_hedges_g <- sd(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE)

# Define the cutoff for outliers (more than 3 standard deviations from the mean)
lower_bound <- mean_hedges_g - 3 * sd_hedges_g
upper_bound <- mean_hedges_g + 3 * sd_hedges_g

# Identify outliers
ma_feedback_time_data_analysis$outlier_prereg <- with(ma_feedback_time_data_analysis, hedges_g < lower_bound | hedges_g > upper_bound)

# Output the studies flagged as outliers
outliers <- ma_feedback_time_data_analysis[ma_feedback_time_data_analysis$outlier_prereg,]
print(outliers)

# Create the histogram
outliers_check_histogram_plot.png <- ggplot(ma_feedback_time_data_analysis, aes(x = hedges_g, fill = as.factor(outlier_prereg))) +
  geom_histogram(binwidth = 0.1, color = "black", alpha = 0.7) +
  geom_vline(xintercept = mean_hedges_g, linetype = "dashed", color = "black", size = 1, label = "Mean") +
  geom_vline(xintercept = lower_bound, linetype = "dotted", color = "#D55E00", size = 1, label = "-3 SD") +
  geom_vline(xintercept = upper_bound, linetype = "dotted", color = "#D55E00", size = 1, label = "+3 SD") +
  scale_fill_manual(values = c("FALSE" = "#0072B2", "TRUE" = "#CC79A7"),  # Using color-blind friendly colors
                    name = "", 
                    labels = c("FALSE" = "Non-Outlier", "TRUE" = "Outlier")) +
  labs(title = "",
       subtitle = paste0("Mean: ", round(mean_hedges_g, 3), ", SD: ", round(sd_hedges_g, 3)),
       x = "Hedges' g", 
       y = "Frequency") +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 16, color = "black"),
    plot.subtitle = element_text(face = "plain", size = 14, color = "grey70"),
    legend.title = element_text(face = "bold", color = "black"),
    legend.text = element_text(size = 12),
    axis.title = element_text(face = "bold", size = 14, color = "black"),
    axis.text = element_text(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    legend.background = element_rect(fill = "white", color = NA),
    legend.box.background = element_rect(color = "grey80"),
    legend.box.margin = margin(5, 5, 5, 5)
  )

# Print the histogram plot
print(outliers_check_histogram_plot.png)

# Save the plot as an image
ggsave("outliers_check_histogram_plot.png", plot = outliers_check_histogram_plot.png, width = 10, height = 8, dpi = 300)

# Remove outliers from the data for further analysis
data_clean <- ma_feedback_time_data_analysis[!ma_feedback_time_data_analysis$outlier_prereg,]

```
#### outliers plot with direction

```{r}
# Calculate the mean and standard deviation of Hedges' g
mean_hedges_g <- mean(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE)
sd_hedges_g <- sd(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE)

# Define the cutoff for outliers (more than 3 standard deviations from the mean)
lower_bound <- mean_hedges_g - 3 * sd_hedges_g
upper_bound <- mean_hedges_g + 3 * sd_hedges_g

# Identify outliers
ma_feedback_time_data_analysis$outlier_prereg <- with(ma_feedback_time_data_analysis, hedges_g < lower_bound | hedges_g > upper_bound)

# Output the studies flagged as outliers
outliers <- ma_feedback_time_data_analysis[ma_feedback_time_data_analysis$outlier_prereg,]
print(outliers)

# Get min value for positioning labels
min_y <- 0

# Create the histogram
outliers_check_histogram_plot.png <- ggplot(ma_feedback_time_data_analysis, aes(x = hedges_g, fill = as.factor(outlier_prereg))) +
  geom_histogram(binwidth = 0.1, color = "black", alpha = 0.7) +
  geom_vline(xintercept = mean_hedges_g, linetype = "dashed", color = "black", size = 1, label = "Mean") +
  geom_vline(xintercept = lower_bound, linetype = "dotted", color = "#D55E00", size = 1, label = "-3 SD") +
  geom_vline(xintercept = upper_bound, linetype = "dotted", color = "#D55E00", size = 1, label = "+3 SD") +
  scale_fill_manual(values = c("FALSE" = "#0072B2", "TRUE" = "#CC79A7"),
                    name = "", 
                    labels = c("FALSE" = "Non-Outlier", "TRUE" = "Outlier")) +
  labs(title = "",
       subtitle = paste0("Mean: ", round(mean_hedges_g, 3), ", SD: ", round(sd_hedges_g, 3)),
       x = "Hedges' g", 
       y = "Frequency") +
  # Add arrows pointing outward from center
  geom_segment(aes(x = 0, y = min_y - 0.5, 
                   xend = max(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE), 
                   yend = min_y - 0.5), 
               arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
  geom_segment(aes(x = 0, y = min_y - 0.5, 
                   xend = min(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE), 
                   yend = min_y - 0.5), 
               arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
  # Add text labels below the arrows
  annotate("text", x = max(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE) / 2, 
           y = min_y - 1.5, 
           label = "Favours immediate feedback", hjust = 0.5, color = "#893F45", size = 6) +
  annotate("text", x = min(ma_feedback_time_data_analysis$hedges_g, na.rm = TRUE) / 2, 
           y = min_y - 1.5, 
           label = "Favours delayed feedback", hjust = 0.5, color = "#893F45", size = 6) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 16, color = "black"),
    plot.subtitle = element_text(face = "plain", size = 14, color = "grey70"),
    legend.title = element_text(face = "bold", color = "black"),
    legend.text = element_text(size = 12),
    axis.title = element_text(face = "bold", size = 14, color = "black"),
    axis.text = element_text(color = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    legend.background = element_rect(fill = "white", color = NA),
    legend.box.background = element_rect(color = "grey80"),
    legend.box.margin = margin(5, 5, 5, 5)
  ) +
  plot_theme

# Print the histogram plot
print(outliers_check_histogram_plot.png)

# Save the plot as an image
ggsave("fig_outliers_check_histogram_plot.png", plot = outliers_check_histogram_plot.png, width = 10, height = 8, dpi = 300)

# Remove outliers from the data for further analysis
data_clean <- ma_feedback_time_data_analysis[!ma_feedback_time_data_analysis$outlier_prereg,]
```

## 4.b- Re-pooling effect sizes without outliers

```{r}
g_feedback_time_corr_without_outliers  <-  robu(formula = hedges_g ~ 1, data = data_clean,
                            studynum = unique_ID, var.eff.size = vi_g,
                            rho = rho,  modelweights = "CORR", small = FALSE)
g_feedback_time_corr_without_outliers

# sensitivity analysis for different rho
sensitivity_table=sensitivity(g_feedback_time_corr_without_outliers)

# Generate the LaTeX table using kable and kableExtra
latex_table_sensitivity <- kable(
  sensitivity_table, 
  format = "latex", 
  booktabs = TRUE, 
  align = "lcccccc"
) %>%
  kable_styling(latex_options = c("hold_position")) %>% # No 'striped' option
  add_header_above(c(" " = 1, "Sensitivity Analysis RVE Model" = 6)) 

# Write the LaTeX table to a .tex file
tex_filename <- normalizePath(file.path(file_path, "sensitivity_rve.tex"), mustWork = FALSE)
tryCatch({
  cat(latex_table_sensitivity, file = tex_filename)
  if (file.exists(tex_filename)) {
    message("File successfully created: ", tex_filename)
  } else {
    warning("Failed to create file: ", tex_filename)
  }
}, error = function(e) {
  warning("An error occurred while writing file: ", e$message)
})


# Print the LaTeX table to console
cat(latex_table_sensitivity)



# Extract for Latex
# Extract reg_table from your model
reg_table <- g_feedback_time_corr_without_outliers$reg_table

# Number of effect sizes (k)
k <- nrow(g_feedback_time_corr_without_outliers$data.full)

# Main description for the subset
subset_description <- "Immediate vs. delayed feedback"

# Assuming reg_table is derived from your 'robu' model
# We'll place each value in its corresponding column now
results_table <- tibble(
  Statistic = c(
    "Immediate vs. delayed feedback", 
    "Num. Obs.", "N", "rho", "I^2", "tau^2"
  ),
  Estimate = c(
    as.character(round(g_feedback_time_corr_without_outliers$reg_table$b.r, 2)),  # g value
    as.character(nrow(g_feedback_time_corr_without_outliers$data.full)),  # Num. Obs.
    as.character(length(unique(g_feedback_time_corr_without_outliers$data.full$study))),  # N
    as.character(g_feedback_time_corr_without_outliers$mod_info$rho),  # rho
    as.character(format(g_feedback_time_corr_without_outliers$mod_info$I.2, digits = 2)),  # I^2
    as.character(format(g_feedback_time_corr_without_outliers$mod_info$tau.sq, digits = 4))  # tau^2
  ),
  `Std. Error` = c(
    as.character(round(g_feedback_time_corr_without_outliers$reg_table$SE, 2)),  # SE value
    "", "", "", "", ""  # Empty for additional stats
  ),
  `t Statistic` = c(
    as.character(round(g_feedback_time_corr_without_outliers$reg_table$t, 2)),  # t value
    "", "", "", "", ""  # Empty for additional stats
  ),
  `P value` = c(
    format.pval(g_feedback_time_corr_without_outliers$reg_table$prob, digits = 3, eps = 0.001, na.form = "<.001"),  # P-value
    "", "", "", "", ""  # Empty for additional stats
  ),
  `95% CI` = c(
    paste0("[", round(g_feedback_time_corr_without_outliers$reg_table$CI.L, 2), ", ", round(g_feedback_time_corr_without_outliers$reg_table$CI.U, 2), "]"),  # 95% CI
    "", "", "", "", ""  # Empty for additional stats
  ),
  `Sig` = c(
    g_feedback_time_corr_without_outliers$reg_table$sig,  # Significance
    "", "", "", "", ""  # Empty for additional stats
  )
)

# Create the LaTeX table using kableExtra
latex_table <- results_table %>%
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "lllllll",  # Alignment for each column
    col.names = c("Statistic", "Estimate", "Std. Error", "t Statistic", "P value", "95% CI", "Sig")
  ) %>%
  kable_styling(
    latex_options = c("hold_position"),
    full_width = FALSE
  ) %>%
  add_header_above(c(" " = 1, "Robust Variance Estimates Model" = 6)) %>%
  row_spec(
    0,  # Insert a horizontal line after the description of the subset
    extra_latex_after = "\\midrule"
  )

# Write the LaTeX table to a .tex file
tex_filename <- normalizePath(file.path(file_path, "model_without_outlier.tex"), mustWork = FALSE)
tryCatch({
  cat(latex_table, file = tex_filename)
  if (file.exists(tex_filename)) {
    message("File successfully created: ", tex_filename)
  } else {
    warning("Failed to create file: ", tex_filename)
  }
}, error = function(e) {
  warning("An error occurred while writing file: ", e$message)
})

# Print the LaTeX table
cat(latex_table)
```
## 4.c Influence Anlaysis (Leave one out)

```{r}
library(robumeta)
library(dplyr)
library(tibble)

# Get unique study IDs
unique_studies <- unique(data_clean$unique_ID)

# Function to run meta-analysis excluding one study
run_loo_analysis <- function(excluded_study, data, rho_value) {
  # Filter out the excluded study
  data_loo <- data %>% filter(unique_ID != excluded_study)
  
  # Run meta-analysis
  model <- robu(formula = hedges_g ~ 1, 
                data = data_loo,
                studynum = unique_ID, 
                var.eff.size = vi_g,
                rho = rho_value,  
                modelweights = "CORR", 
                small = FALSE)
  
  # Extract key statistics
  results <- tibble(
    excluded_study = excluded_study,
    estimate = model$reg_table$b.r,
    se = model$reg_table$SE,
    ci_lower = model$reg_table$CI.L,
    ci_upper = model$reg_table$CI.U,
    p_value = model$reg_table$prob,
    tau_squared = model$mod_info$tau.sq,
    I_squared = model$mod_info$I.2,
    n_studies = model$N,
    n_effects = model$M
  )
  
  return(results)
}

# Run leave-one-out analysis for all studies
influence_results <- map_df(unique_studies, 
                            ~run_loo_analysis(.x, data_clean, rho = rho))

# View results
print(influence_results, n = Inf)

# Optional: Calculate change from original model
original_estimate <- g_feedback_time_corr_without_outliers$reg_table$b.r

influence_results <- influence_results %>%
  mutate(
    estimate_change = estimate - original_estimate,
    percent_change = ((estimate - original_estimate) / original_estimate) * 100
  )

# Identify most influential studies (largest absolute change)
most_influential <- influence_results %>%
  arrange(desc(abs(estimate_change))) %>%
  select(excluded_study, estimate, estimate_change, percent_change, 
         ci_lower, ci_upper, p_value, n_studies, n_effects)

print(most_influential)

# Optional: Save to CSV for appendix
write.csv(influence_results, "influence_analysis_results.csv", row.names = FALSE)

# Print min and max for manuscript text
min_estimate <- min(influence_results$estimate)
max_estimate <- max(influence_results$estimate)

cat("\n=== FOR MANUSCRIPT ===\n")
cat(sprintf("Min estimate: g = %.3f\n", min_estimate))
cat(sprintf("Max estimate: g = %.3f\n", max_estimate))
cat(sprintf("Original estimate: g = %.3f\n", original_estimate))
cat(sprintf("\nRange of estimates: g = %.3f to g = %.3f\n", min_estimate, max_estimate))
cat("\nCopy this for your manuscript:\n")
cat(sprintf("The leave-one-study-out influence analysis showed that the overall effect estimate ranged from g = %.3f to g = %.3f when individual studies were sequentially removed, indicating robust findings not driven by any single study; see Appendix~\\ref{secA8} for detailed results.\n", min_estimate, max_estimate))

# Create publication-ready table
influence_table <- influence_results %>%
  mutate(
    `Effect Size` = sprintf("%.3f", estimate),
    `95% CI` = sprintf("[%.3f, %.3f]", ci_lower, ci_upper),
    `p` = ifelse(p_value < .001, "< .001", sprintf("%.3f", p_value)),
    `Δg` = sprintf("%+.3f", estimate_change)
  ) %>%
  select(`Excluded Study` = excluded_study, 
         k = n_studies,
         `Effect Size`,
         `95% CI`,
         `p`,
         `Δg`)

print(influence_table, n = Inf)

# Save for manuscript
write.csv(influence_table, "table_influence_analysis.csv", row.names = FALSE)

# Summary table for most influential studies (for appendix)
influential_summary <- influence_results %>%
  arrange(desc(abs(estimate_change))) %>%
  mutate(
    estimate = round(estimate, 3),
    ci_lower = round(ci_lower, 3),
    ci_upper = round(ci_upper, 3),
    estimate_change = round(estimate_change, 3),
    percent_change = round(percent_change, 2),
    p_value = round(p_value, 3),
    CI_95 = paste0("[", ci_lower, ", ", ci_upper, "]")
  ) %>%
  select(excluded_study, estimate, CI_95, estimate_change, 
         percent_change, p_value, n_studies, n_effects)

print(influential_summary)

# Save summary table
write.csv(influential_summary, "influence_analysis_summary.csv", row.names = FALSE)

# Prepare data with significance indicator
influence_plot_data <- influence_results %>%
  mutate(
    significant = ifelse(p_value < 0.05, "Significant (p < .05)", "Non-significant (p ≥ .05)"),
    significant = factor(significant, levels = c("Significant (p < .05)", "Non-significant (p ≥ .05)"))
  )

# Create influence plot matching correlation plot style
influence_plot_range <- ggplot(influence_plot_data, 
                               aes(y = reorder(excluded_study, estimate), 
                                   x = estimate, 
                                   color = significant)) +
  geom_vline(xintercept = original_estimate, 
             linetype = "dashed", 
             color = "black", 
             linewidth = 0.8) +
  geom_point(size = 3, alpha = 0.8) +
  scale_color_manual(values = c("Significant (p < .05)" = "#D55E00", 
                                 "Non-significant (p ≥ .05)" = "#5A75AA"),
                     labels = c("Significant (p < .05)" = expression(paste("Significant (", italic(p), " < .05)")),
                                "Non-significant (p ≥ .05)" = expression(paste("Non-significant (", italic(p), " ≥ .05)"))),
                     name = "") +
  scale_y_discrete(expand = expansion(add = 0.8)) +  # Add space between studies
  labs(y = "", 
       x = "Effect Size (Hedges' g)") +
  plot_theme +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 10)
  )
print(influence_plot_range)
ggsave("fig_influence_analysis.png", 
       plot = influence_plot_range, 
       width = 6,    
       height = 9,   # Made plot longer for more spacing
       dpi = 300, 
       bg = "white")
```

## 4.d Sensitivity Analysis
```{r}
# SENSITIVITY ANALYSIS: Excluding short delays
# Time delays < 1 minute OR item delays < 5 items

# First, let's examine the delay structure
cat("\n=== Original Data Summary ===\n")
cat("Total effects:", nrow(data_clean), "\n")
cat("Delay definitions:\n")
print(table(data_clean$delay_definition, useNA = "ifany"))

# Create a filtering criterion based on delay type
data_clean <- data_clean %>%
  mutate(
    # Identify effects to EXCLUDE (short delays)
    exclude_short_delay = case_when(
      delay_definition == "seconds" & delay_d.seconds.item. < 60 ~ TRUE,
      delay_definition == "item" & delay_d.seconds.item. < 5 ~ TRUE,
      TRUE ~ FALSE
    )
  )

# Summary of exclusions
cat("\n=== Exclusion Summary ===\n")
cat("Effects with second-based delays < 1 minute:", 
    sum(data_clean$delay_definition == "seconds" & data_clean$delay_d.seconds.item. < 60, na.rm = TRUE), "\n")
cat("Effects with item-based delays < 5 items:", 
    sum(data_clean$delay_definition == "item" & data_clean$delay_d.seconds.item. < 5, na.rm = TRUE), "\n")
cat("Total effects to exclude:", sum(data_clean$exclude_short_delay, na.rm = TRUE), "\n")



cat("\n\n=== DETAILED LIST OF EXCLUDED EFFECTS ===\n\n")

# Get excluded effects
excluded_effects <- data_clean %>%
  filter(exclude_short_delay == TRUE) %>%
  select(unique_ID, g_ID, delay_definition, delay_d.seconds.item., hedges_g) %>%
  arrange(delay_definition, delay_d.seconds.item., unique_ID)

# Print excluded effects with second-based delays
cat("--- SECOND-BASED DELAYS (< 60 seconds) ---\n")
excluded_seconds <- excluded_effects %>%
  filter(delay_definition == "seconds")

if (nrow(excluded_seconds) > 0) {
  cat(sprintf("Total excluded: %d effects from %d unique studies\n\n", 
              nrow(excluded_seconds), 
              length(unique(excluded_seconds$unique_ID))))
  
  for (i in 1:nrow(excluded_seconds)) {
    cat(sprintf("%3d. Study: %-25s Effect ID: %-10s Delay: %6.2f seconds  Hedges' g: %6.3f\n",
                i,
                excluded_seconds$unique_ID[i],
                excluded_seconds$g_ID[i],
                excluded_seconds$delay_d.seconds.item.[i],
                excluded_seconds$hedges_g[i]))
  }
  
  # Summary by study
  cat("\n--- Summary by Study (Second-based) ---\n")
  study_summary_seconds <- excluded_seconds %>%
    group_by(unique_ID) %>%
    summarise(
      n_effects = n(),
      min_delay = min(delay_d.seconds.item.),
      max_delay = max(delay_d.seconds.item.),
      mean_delay = mean(delay_d.seconds.item.)
    ) %>%
    arrange(mean_delay)
  
  print(study_summary_seconds, n = Inf)
} else {
  cat("No effects excluded based on second-based delays < 60 seconds\n")
}

cat("\n\n--- ITEM-BASED DELAYS (< 5 items) ---\n")
excluded_items <- excluded_effects %>%
  filter(delay_definition == "item")

if (nrow(excluded_items) > 0) {
  cat(sprintf("Total excluded: %d effects from %d unique studies\n\n", 
              nrow(excluded_items), 
              length(unique(excluded_items$unique_ID))))
  
  for (i in 1:nrow(excluded_items)) {
    cat(sprintf("%3d. Study: %-25s Effect ID: %-10s Delay: %6.0f items     Hedges' g: %6.3f\n",
                i,
                excluded_items$unique_ID[i],
                excluded_items$g_ID[i],
                excluded_items$delay_d.seconds.item.[i],
                excluded_items$hedges_g[i]))
  }
  
  # Summary by study
  cat("\n--- Summary by Study (Item-based) ---\n")
  study_summary_items <- excluded_items %>%
    group_by(unique_ID) %>%
    summarise(
      n_effects = n(),
      min_delay = min(delay_d.seconds.item.),
      max_delay = max(delay_d.seconds.item.),
      mean_delay = mean(delay_d.seconds.item.)
    ) %>%
    arrange(mean_delay)
  
  print(study_summary_items, n = Inf)
} else {
  cat("No effects excluded based on item-based delays < 5 items\n")
}

# Overall summary
cat("\n\n--- OVERALL EXCLUSION SUMMARY ---\n")
cat(sprintf("Total unique studies excluded: %d\n", length(unique(excluded_effects$unique_ID))))
cat(sprintf("Total effects excluded: %d\n", nrow(excluded_effects)))
cat(sprintf("  - Second-based (< 60 sec): %d effects\n", sum(excluded_effects$delay_definition == "seconds")))
cat(sprintf("  - Item-based (< 5 items): %d effects\n", sum(excluded_effects$delay_definition == "item")))

# Create filtered dataset for sensitivity analysis
data_sensitivity <- data_clean %>%
  filter(!exclude_short_delay)

cat("\n=== Sensitivity Analysis Dataset ===\n")
cat("Effects remaining:", nrow(data_sensitivity), "\n")
cat("Effects excluded:", nrow(data_clean) - nrow(data_sensitivity), "\n")
cat("Unique studies remaining:", length(unique(data_sensitivity$unique_ID)), "\n")
cat("Delay definitions in sensitivity dataset:\n")
print(table(data_sensitivity$delay_definition, useNA = "ifany"))


# RUN SENSITIVITY ANALYSIS MODEL

g_feedback_sensitivity <- robu(
  formula = hedges_g ~ 1, 
  data = data_sensitivity,
  studynum = unique_ID, 
  var.eff.size = vi_g,
  rho = rho,  
  modelweights = "CORR", 
  small = FALSE
)

# Print results
cat("\n=== SENSITIVITY ANALYSIS RESULTS ===\n")
cat("(Excluding time delays < 1 min and item delays < 5 items)\n\n")
print(g_feedback_sensitivity)

# Sensitivity analysis for different rho values
sensitivity_table_sens <- sensitivity(g_feedback_sensitivity)

# Generate the LaTeX table for sensitivity analysis
latex_table_sensitivity_sens <- kable(
  sensitivity_table_sens, 
  format = "latex", 
  booktabs = TRUE, 
  align = "lcccccc"
) %>%
  kable_styling(latex_options = c("hold_position")) %>%
  add_header_above(c(" " = 1, "Sensitivity Analysis (Excluding Short Delays)" = 6))

# Write to file
tex_filename_sens <- normalizePath(
  file.path(file_path, "sensitivity_rve_no_short_delays.tex"), 
  mustWork = FALSE
)
tryCatch({
  cat(latex_table_sensitivity_sens, file = tex_filename_sens)
  if (file.exists(tex_filename_sens)) {
    message("File successfully created: ", tex_filename_sens)
  } else {
    warning("Failed to create file: ", tex_filename_sens)
  }
}, error = function(e) {
  warning("An error occurred while writing file: ", e$message)
})

cat(latex_table_sensitivity_sens)

# CREATE RESULTS TABLE FOR SENSITIVITY ANALYSIS

# Extract reg_table
reg_table_sens <- g_feedback_sensitivity$reg_table

# Number of effect sizes
k_sens <- nrow(g_feedback_sensitivity$data.full)

# Number of unique studies
n_studies_sens <- length(unique(g_feedback_sensitivity$data.full$unique_ID))

# Create results table
results_table_sens <- tibble(
  Statistic = c(
    "Immediate vs. delayed feedback (excluding short delays)", 
    "Num. Obs.", "N", "rho", "I^2", "tau^2"
  ),
  Estimate = c(
    as.character(round(reg_table_sens$b.r, 2)),
    as.character(k_sens),
    as.character(n_studies_sens),
    as.character(g_feedback_sensitivity$mod_info$rho),
    as.character(format(g_feedback_sensitivity$mod_info$I.2, digits = 2)),
    as.character(format(g_feedback_sensitivity$mod_info$tau.sq, digits = 4))
  ),
  `Std. Error` = c(
    as.character(round(reg_table_sens$SE, 2)),
    "", "", "", "", ""
  ),
  `t Statistic` = c(
    as.character(round(reg_table_sens$t, 2)),
    "", "", "", "", ""
  ),
  `P value` = c(
    format.pval(reg_table_sens$prob, digits = 3, eps = 0.001, na.form = "<.001"),
    "", "", "", "", ""
  ),
  `95% CI` = c(
    paste0("[", round(reg_table_sens$CI.L, 2), ", ", 
           round(reg_table_sens$CI.U, 2), "]"),
    "", "", "", "", ""
  ),
  `Sig` = c(
    reg_table_sens$sig,
    "", "", "", "", ""
  )
)

# Create LaTeX table
latex_table_sens <- results_table_sens %>%
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "lllllll",
    col.names = c("Statistic", "Estimate", "Std. Error", "t Statistic", 
                  "P value", "95% CI", "Sig")
  ) %>%
  kable_styling(
    latex_options = c("hold_position"),
    full_width = FALSE
  ) %>%
  add_header_above(c(" " = 1, "Robust Variance Estimates Model (Sensitivity)" = 6)) %>%
  row_spec(0, extra_latex_after = "\\midrule")

# Write to file
tex_filename_model_sens <- normalizePath(
  file.path(file_path, "model_sensitivity_no_short_delays.tex"), 
  mustWork = FALSE
)
tryCatch({
  cat(latex_table_sens, file = tex_filename_model_sens)
  if (file.exists(tex_filename_model_sens)) {
    message("File successfully created: ", tex_filename_model_sens)
  } else {
    warning("Failed to create file: ", tex_filename_model_sens)
  }
}, error = function(e) {
  warning("An error occurred while writing file: ", e$message)
})

cat(latex_table_sens)

# COMPARISON SUMMARY

cat("\n\n=== COMPARISON: Original vs. Sensitivity Analysis ===\n")
comparison_df <- data.frame(
  Model = c("Original (with all delays)", 
            "Sensitivity (excluding short delays)"),
  k = c(nrow(g_feedback_time_corr_without_outliers$data.full), k_sens),
  N_studies = c(length(unique(g_feedback_time_corr_without_outliers$data.full$unique_ID)), 
                n_studies_sens),
  Estimate = c(round(g_feedback_time_corr_without_outliers$reg_table$b.r, 3),
               round(reg_table_sens$b.r, 3)),
  SE = c(round(g_feedback_time_corr_without_outliers$reg_table$SE, 3),
         round(reg_table_sens$SE, 3)),
  CI_Lower = c(round(g_feedback_time_corr_without_outliers$reg_table$CI.L, 3),
               round(reg_table_sens$CI.L, 3)),
  CI_Upper = c(round(g_feedback_time_corr_without_outliers$reg_table$CI.U, 3),
               round(reg_table_sens$CI.U, 3)),
  p_value = c(round(g_feedback_time_corr_without_outliers$reg_table$prob, 4),
              round(reg_table_sens$prob, 4))
)

print(comparison_df)


# SAVE EXCLUDED EFFECTS LIST TO CSV


# Save detailed list to CSV for reference
csv_filename <- normalizePath(
  file.path(file_path, "excluded_effects_sensitivity.csv"), 
  mustWork = FALSE
)

excluded_effects_full <- data_clean %>%
  filter(exclude_short_delay == TRUE) %>%
  select(unique_ID, g_ID, delay_definition, delay_d.seconds.item., 
         hedges_g, se_g, sample_size, year) %>%
  arrange(delay_definition, delay_d.seconds.item., unique_ID)

write.csv(excluded_effects_full, csv_filename, row.names = FALSE)
cat(sprintf("\n\nDetailed list of excluded effects saved to: %s\n", csv_filename))
```

```{r}
# ANALYZE WHICH STUDIES REMAIN AFTER PARTIAL EXCLUSION

cat("\n\n=== STUDY RETENTION ANALYSIS ===\n\n")

# Get unique studies in original data
studies_original <- unique(data_clean$unique_ID)

# Get unique studies with excluded effects
studies_with_exclusions <- unique(data_clean$unique_ID[data_clean$exclude_short_delay == TRUE])

# Get unique studies remaining in sensitivity analysis
studies_in_sensitivity <- unique(data_sensitivity$unique_ID)

# Studies that were partially excluded (some effects removed, but study remains)
studies_partially_excluded <- intersect(studies_with_exclusions, studies_in_sensitivity)

# Studies that were completely excluded (all effects removed)
studies_completely_excluded <- setdiff(studies_with_exclusions, studies_in_sensitivity)

cat("--- SUMMARY ---\n")
cat("Total unique studies in original data:", length(studies_original), "\n")
cat("Studies with at least one excluded effect:", length(studies_with_exclusions), "\n")
cat("Studies PARTIALLY excluded (some effects removed, study remains):", length(studies_partially_excluded), "\n")
cat("Studies COMPLETELY excluded (all effects removed):", length(studies_completely_excluded), "\n")
cat("Studies remaining in sensitivity analysis:", length(studies_in_sensitivity), "\n")

# DETAILED VIEW: PARTIALLY EXCLUDED STUDIES

if (length(studies_partially_excluded) > 0) {
  cat("\n\n--- STUDIES PARTIALLY EXCLUDED (Study remains but lost some effects) ---\n\n")
  
  for (study in studies_partially_excluded) {
    # Get all effects for this study
    study_effects_original <- data_clean %>% 
      filter(unique_ID == study)
    
    study_effects_excluded <- study_effects_original %>% 
      filter(exclude_short_delay == TRUE)
    
    study_effects_retained <- study_effects_original %>% 
      filter(exclude_short_delay == FALSE)
    
    cat(sprintf("\nStudy: %s\n", study))
    cat(sprintf("  Total effects: %d\n", nrow(study_effects_original)))
    cat(sprintf("  Effects excluded: %d\n", nrow(study_effects_excluded)))
    cat(sprintf("  Effects retained: %d\n", nrow(study_effects_retained)))
    cat(sprintf("  Delay definition: %s\n", unique(study_effects_original$delay_definition)[1]))
    
    cat("\n  Excluded effects:\n")
    for (i in 1:nrow(study_effects_excluded)) {
      cat(sprintf("    - %s: delay = %.2f %s, g = %.3f\n",
                  study_effects_excluded$g_ID[i],
                  study_effects_excluded$delay_d.seconds.item.[i],
                  ifelse(study_effects_excluded$delay_definition[i] == "seconds", "seconds", "items"),
                  study_effects_excluded$hedges_g[i]))
    }
    
    cat("\n  Retained effects:\n")
    for (i in 1:nrow(study_effects_retained)) {
      cat(sprintf("    - %s: delay = %.2f %s, g = %.3f\n",
                  study_effects_retained$g_ID[i],
                  study_effects_retained$delay_d.seconds.item.[i],
                  ifelse(study_effects_retained$delay_definition[i] == "seconds", "seconds", "items"),
                  study_effects_retained$hedges_g[i]))
    }
  }
}

# DETAILED VIEW: COMPLETELY EXCLUDED STUDIES

if (length(studies_completely_excluded) > 0) {
  cat("\n\n--- STUDIES COMPLETELY EXCLUDED (All effects removed) ---\n\n")
  
  for (study in studies_completely_excluded) {
    study_effects <- data_clean %>% 
      filter(unique_ID == study)
    
    cat(sprintf("\nStudy: %s\n", study))
    cat(sprintf("  Total effects (all excluded): %d\n", nrow(study_effects)))
    cat(sprintf("  Delay definition: %s\n", unique(study_effects$delay_definition)[1]))
    cat(sprintf("  Delay range: %.2f to %.2f %s\n",
                min(study_effects$delay_d.seconds.item.),
                max(study_effects$delay_d.seconds.item.),
                ifelse(unique(study_effects$delay_definition)[1] == "seconds", "seconds", "items")))
    
    cat("\n  All excluded effects:\n")
    for (i in 1:nrow(study_effects)) {
      cat(sprintf("    - %s: delay = %.2f %s, g = %.3f\n",
                  study_effects$g_ID[i],
                  study_effects$delay_d.seconds.item.[i],
                  ifelse(study_effects$delay_definition[i] == "seconds", "seconds", "items"),
                  study_effects$hedges_g[i]))
    }
  }
}


# CREATE SUMMARY TABLE


cat("\n\n--- SUMMARY TABLE BY STUDY ---\n")

summary_by_study <- data_clean %>%
  group_by(unique_ID) %>%
  summarise(
    total_effects = n(),
    excluded_effects = sum(exclude_short_delay),
    retained_effects = sum(!exclude_short_delay),
    delay_definition = first(delay_definition),
    min_delay = min(delay_d.seconds.item.),
    max_delay = max(delay_d.seconds.item.),
    status = case_when(
      excluded_effects == 0 ~ "Fully retained",
      retained_effects == 0 ~ "Completely excluded",
      TRUE ~ "Partially excluded"
    )
  ) %>%
  arrange(status, delay_definition, unique_ID)

print(summary_by_study, n = Inf)


# SAVE TO CSV


csv_filename_summary <- normalizePath(
  file.path(file_path, "study_exclusion_summary.csv"), 
  mustWork = FALSE
)

write.csv(summary_by_study, csv_filename_summary, row.names = FALSE)
cat(sprintf("\n\nStudy exclusion summary saved to: %s\n", csv_filename_summary))


# QUICK REFERENCE LISTS


cat("\n\n=== QUICK REFERENCE ===\n")

cat("\nStudies PARTIALLY excluded (", length(studies_partially_excluded), " studies):\n", sep = "")
cat(paste(studies_partially_excluded, collapse = ", "), "\n")

cat("\nStudies COMPLETELY excluded (", length(studies_completely_excluded), " studies):\n", sep = "")
if (length(studies_completely_excluded) > 0) {
  cat(paste(studies_completely_excluded, collapse = ", "), "\n")
} else {
  cat("None\n")
}
```


## 4.e. Categorical Meta Analysis

```{r}

# CATEGORICAL META-ANALYSIS: Short, Intermediate, and Long Delays


# First, create the delay categories based on the table you provided
data_clean <- data_clean %>%
  mutate(
    delay_category = case_when(
      # Second-based delays
      delay_definition == "seconds" & delay_d.seconds.item. < 3600 ~ "Short",  # < 1 hour (3600 seconds)
      delay_definition == "seconds" & delay_d.seconds.item. >= 3600 & delay_d.seconds.item. <= 86400 ~ "Intermediate",  # 1 hour to 1 day (86400 seconds)
      delay_definition == "seconds" & delay_d.seconds.item. > 86400 ~ "Long",  # > 1 day
      
      # Item-based delays
      delay_definition == "item" & delay_d.seconds.item. <= 10 ~ "Short",  # 1-10 items
      delay_definition == "item" & delay_d.seconds.item. > 10 & delay_d.seconds.item. <= 30 ~ "Intermediate",  # 11-30 items
      delay_definition == "item" & delay_d.seconds.item. > 30 ~ "Long",  # > 30 items
      
      TRUE ~ NA_character_
    )
  )

# Check the categorization
cat("\n=== DELAY CATEGORIZATION ===\n")
cat("\nOverall distribution:\n")
print(table(data_clean$delay_category, useNA = "ifany"))

cat("\nBy delay definition:\n")
print(table(data_clean$delay_definition, data_clean$delay_category, useNA = "ifany"))

# Summary statistics by category
cat("\n\n--- Summary by Delay Category ---\n")
category_summary <- data_clean %>%
  group_by(delay_category, delay_definition) %>%
  summarise(
    n_effects = n(),
    n_studies = n_distinct(unique_ID),
    min_delay = min(delay_d.seconds.item.),
    max_delay = max(delay_d.seconds.item.),
    mean_delay = mean(delay_d.seconds.item.),
    median_delay = median(delay_d.seconds.item.),
    .groups = "drop"
  ) %>%
  arrange(delay_category, delay_definition)

print(category_summary, n = Inf)


# RUN CATEGORICAL META-ANALYSIS MODELS


cat("\n\n=== CATEGORICAL META-ANALYSIS MODELS ===\n\n")

# Model with delay_category as moderator
g_feedback_categorical <- robu(
  formula = hedges_g ~ 0 + delay_category,  # 0 removes intercept to get estimates for each category
  data = data_clean,
  studynum = unique_ID, 
  var.eff.size = vi_g,
  rho = rho,  
  modelweights = "CORR", 
  small = FALSE
)

cat("--- Categorical Model Results ---\n")
print(g_feedback_categorical)

# Extract results for each category
reg_table_cat <- g_feedback_categorical$reg_table

# Also run models for each category separately to get heterogeneity stats
cat("\n\n--- Individual Category Models ---\n\n")

categories <- c("Short", "Intermediate", "Long")
category_results <- list()

for (cat_name in categories) {
  cat(sprintf("\n=== %s Delays ===\n", cat_name))
  
  data_cat <- data_clean %>% filter(delay_category == cat_name)
  
  if (nrow(data_cat) > 0) {
    model_cat <- robu(
      formula = hedges_g ~ 1,
      data = data_cat,
      studynum = unique_ID,
      var.eff.size = vi_g,
      rho = rho,
      modelweights = "CORR",
      small = FALSE
    )
    
    print(model_cat)
    
    # Store results
    category_results[[cat_name]] <- list(
      model = model_cat,
      n_effects = nrow(data_cat),
      n_studies = length(unique(data_cat$unique_ID)),
      estimate = model_cat$reg_table$b.r,
      se = model_cat$reg_table$SE,
      ci_lower = model_cat$reg_table$CI.L,
      ci_upper = model_cat$reg_table$CI.U,
      p_value = model_cat$reg_table$prob,
      tau_sq = model_cat$mod_info$tau.sq,
      I2 = model_cat$mod_info$I.2
    )
  } else {
    cat("No data in this category\n")
    category_results[[cat_name]] <- NULL
  }
}


# CREATE RESULTS TABLE FOR CATEGORICAL ANALYSIS (INCLUDING OVERALL)


cat("\n\n=== CREATING RESULTS TABLE ===\n")

# Create comprehensive results table
results_categorical <- tibble(
  Category = character(),
  k = integer(),
  N = integer(),
  Estimate = numeric(),
  SE = numeric(),
  CI_Lower = numeric(),
  CI_Upper = numeric(),
  p_value = numeric(),
  tau_sq = numeric(),
  I2 = numeric()
)

# Add individual category results
for (cat_name in categories) {
  if (!is.null(category_results[[cat_name]])) {
    results_categorical <- results_categorical %>%
      add_row(
        Category = cat_name,
        k = category_results[[cat_name]]$n_effects,
        N = category_results[[cat_name]]$n_studies,
        Estimate = category_results[[cat_name]]$estimate,
        SE = category_results[[cat_name]]$se,
        CI_Lower = category_results[[cat_name]]$ci_lower,
        CI_Upper = category_results[[cat_name]]$ci_upper,
        p_value = category_results[[cat_name]]$p_value,
        tau_sq = category_results[[cat_name]]$tau_sq,
        I2 = category_results[[cat_name]]$I2
      )
  }
}

# Add overall effect
overall_counts <- data_clean %>%
  summarise(
    n_studies = n_distinct(unique_ID),
    n_effects = n()
  )

results_categorical <- results_categorical %>%
  add_row(
    Category = "Overall",
    k = overall_counts$n_effects,
    N = overall_counts$n_studies,
    Estimate = g_feedback_time_corr_without_outliers$reg_table$b.r,
    SE = g_feedback_time_corr_without_outliers$reg_table$SE,
    CI_Lower = g_feedback_time_corr_without_outliers$reg_table$CI.L,
    CI_Upper = g_feedback_time_corr_without_outliers$reg_table$CI.U,
    p_value = g_feedback_time_corr_without_outliers$reg_table$prob,
    tau_sq = g_feedback_time_corr_without_outliers$mod_info$tau.sq,
    I2 = g_feedback_time_corr_without_outliers$mod_info$I.2
  )

print(results_categorical)


# CREATE LATEX TABLE FOR CATEGORICAL RESULTS (WITH OVERALL)


# Format the results table for LaTeX
results_categorical_formatted <- results_categorical %>%
  mutate(
    Estimate_fmt = sprintf("%.2f", Estimate),
    SE_fmt = sprintf("%.2f", SE),
    CI_fmt = sprintf("[%.2f, %.2f]", CI_Lower, CI_Upper),
    p_fmt = format.pval(p_value, digits = 3, eps = 0.001),
    tau_sq_fmt = sprintf("%.4f", tau_sq),
    I2_fmt = sprintf("%.2f%%", I2)
  ) %>%
  select(Category, k, N, Estimate_fmt, SE_fmt, CI_fmt, p_fmt, tau_sq_fmt, I2_fmt)

latex_table_categorical <- results_categorical_formatted %>%
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "lcccccccc",
    col.names = c("Delay Category", "k", "N", "Estimate", "SE", "95% CI", "p", "$\\tau^2$", "$I^2$"),
    escape = FALSE
  ) %>%
  kable_styling(
    latex_options = c("hold_position"),
    full_width = FALSE
  ) %>%
  add_header_above(c(" " = 1, "Sample" = 2, "Effect Size" = 4, "Heterogeneity" = 2)) %>%
  # Add horizontal line before Overall row
  row_spec(nrow(results_categorical_formatted) - 1, hline_after = TRUE) %>%
  # Make Overall row bold
  row_spec(nrow(results_categorical_formatted), bold = TRUE) %>%
  footnote(
    general = c(
      "Short delays: seconds < 1 hour or items 1-10",
      "Intermediate delays: seconds 1 hour-1 day or items 11-30", 
      "Long delays: seconds > 1 day or items > 30",
      sprintf("Overall model rho = %.2f", rho)
    ),
    general_title = "Note:",
    footnote_as_chunk = TRUE,
    escape = FALSE
  )

# Write to file
tex_filename_categorical <- normalizePath(
  file.path(file_path, "tab_categorical_meta_analysis.tex"), 
  mustWork = FALSE
)
tryCatch({
  cat(latex_table_categorical, file = tex_filename_categorical)
  if (file.exists(tex_filename_categorical)) {
    message("Categorical results table saved: ", tex_filename_categorical)
  }
}, error = function(e) {
  warning("Error writing categorical table: ", e$message)
})

cat("\n")
cat(latex_table_categorical)


# PREPARE DATA FOR FOREST PLOT WITH SUBGROUPS


cat("\n\n=== PREPARING FOREST PLOT DATA ===\n")

# Prepare data for forest plot
# We need effect sizes, variance, study labels, and categories
forest_data <- data_clean %>%
  mutate(
    study_label = paste0(unique_ID, " (", g_ID, ")"),
    delay_category = factor(delay_category, levels = c("Short", "Intermediate", "Long"))
  ) %>%
  arrange(delay_category, unique_ID, g_ID) %>%
  select(study_label, unique_ID, g_ID, hedges_g, se_g, vi_g, delay_category, 
         delay_definition, delay_d.seconds.item.)

# Add pooled estimates for each subgroup
pooled_estimates <- results_categorical %>%
  filter(Category != "Overall") %>%  # Exclude overall for now
  mutate(
    study_label = paste0(Category, " delays (pooled)"),
    unique_ID = paste0("POOLED_", Category),
    g_ID = "pooled",
    hedges_g = Estimate,
    se_g = SE,
    vi_g = SE^2,
    delay_category = factor(Category, levels = c("Short", "Intermediate", "Long")),
    delay_definition = NA_character_,
    delay_d.seconds.item. = NA_real_,
    is_pooled = TRUE
  ) %>%
  select(study_label, unique_ID, g_ID, hedges_g, se_g, vi_g, delay_category,
         delay_definition, delay_d.seconds.item., is_pooled)

# Add is_pooled flag to forest_data
forest_data <- forest_data %>%
  mutate(is_pooled = FALSE)

# Combine individual studies with pooled estimates
forest_data_combined <- bind_rows(forest_data, pooled_estimates) %>%
  arrange(delay_category, !is_pooled, unique_ID)

# Calculate overall pooled effect (from results_categorical)
overall_pooled <- results_categorical %>%
  filter(Category == "Overall") %>%
  mutate(
    study_label = "Overall effect",
    unique_ID = "OVERALL",
    g_ID = "overall",
    hedges_g = Estimate,
    se_g = SE,
    vi_g = SE^2,
    delay_category = NA,
    delay_definition = NA_character_,
    delay_d.seconds.item. = NA_real_,
    is_pooled = TRUE
  ) %>%
  select(study_label, unique_ID, g_ID, hedges_g, se_g, vi_g, delay_category,
         delay_definition, delay_d.seconds.item., is_pooled)

forest_data_final <- bind_rows(forest_data_combined, overall_pooled)

cat("Forest plot data prepared with", nrow(forest_data_final), "rows\n")
cat("  Individual effects:", sum(!forest_data_final$is_pooled, na.rm = TRUE), "\n")
cat("  Subgroup pooled estimates:", sum(forest_data_final$is_pooled & !is.na(forest_data_final$delay_category), na.rm = TRUE), "\n")
cat("  Overall pooled estimate: 1\n")


# CREATE FOREST PLOT WITH SUBGROUPS


cat("\n\n=== CREATING FOREST PLOT ===\n")

library(metafor)

# Calculate confidence intervals
forest_data_final <- forest_data_final %>%
  mutate(
    ci_lower = hedges_g - 1.96 * se_g,
    ci_upper = hedges_g + 1.96 * se_g
  )

# Create the forest plot
pdf(file.path(file_path, "forest_plot_categorical.pdf"), width = 12, height = max(8, nrow(forest_data_final) * 0.3))

par(mar = c(5, 4, 4, 2))

# Set up the plot area
rows_total <- nrow(forest_data_final)
row_positions <- rows_total:1

# Determine which rows are subgroup headers and pooled estimates
subgroup_rows <- which(!is.na(forest_data_final$delay_category) & forest_data_final$is_pooled)
overall_row <- which(forest_data_final$unique_ID == "OVERALL")

# Create forest plot using metafor
forest(
  x = forest_data_final$hedges_g,
  vi = forest_data_final$vi_g,
  slab = forest_data_final$study_label,
  xlab = "Hedges' g",
  mlab = "",
  ilab = cbind(
    ifelse(forest_data_final$is_pooled, "", 
           sprintf("%.2f", forest_data_final$delay_d.seconds.item.))
  ),
  ilab.xpos = c(-1.5),
  ilab.pos = 4,
  cex = 0.75,
  xlim = c(-3, 3),
  alim = c(-1, 1),
  refline = 0,
  rows = row_positions,
  psize = 1,
  header = c("Study", "Hedges' g [95% CI]"),
  top = 2
)

# Add column header for delay
text(-1.5, rows_total + 2, "Delay", cex = 0.75, font = 2)

# Highlight pooled estimates with different symbols
points(forest_data_final$hedges_g[subgroup_rows], 
       row_positions[subgroup_rows], 
       pch = 18, cex = 1.5, col = "blue")

points(forest_data_final$hedges_g[overall_row], 
       row_positions[overall_row], 
       pch = 18, cex = 2, col = "red")

# Add subgroup labels
short_start <- min(which(forest_data_final$delay_category == "Short" & !forest_data_final$is_pooled))
intermediate_start <- min(which(forest_data_final$delay_category == "Intermediate" & !forest_data_final$is_pooled))
long_start <- min(which(forest_data_final$delay_category == "Long" & !forest_data_final$is_pooled))

text(-3, row_positions[short_start] + 0.5, "Short Delays", pos = 4, font = 2, cex = 0.8)
text(-3, row_positions[intermediate_start] + 0.5, "Intermediate Delays", pos = 4, font = 2, cex = 0.8)
text(-3, row_positions[long_start] + 0.5, "Long Delays", pos = 4, font = 2, cex = 0.8)

dev.off()

cat("Forest plot saved to:", file.path(file_path, "forest_plot_categorical.pdf"), "\n")


# ALTERNATIVE: CREATE A CLEANER FOREST PLOT USING BASE PLOTTING


cat("\n\n=== CREATING ENHANCED FOREST PLOT ===\n")

pdf(file.path(file_path, "forest_plot_categorical_enhanced.pdf"), width = 14, height = max(10, nrow(forest_data_final) * 0.25))

# Calculate plot dimensions
n_rows <- nrow(forest_data_final)
y_positions <- n_rows:1

# Set up plotting area with more space
par(mar = c(5, 25, 4, 2), xpd = FALSE)

# Determine x-axis limits
x_min <- min(forest_data_final$ci_lower, na.rm = TRUE) - 0.2
x_max <- max(forest_data_final$ci_upper, na.rm = TRUE) + 0.2

# Create empty plot
plot(0, 0, type = "n", 
     xlim = c(x_min, x_max), 
     ylim = c(0, n_rows + 3),
     xlab = "Hedges' g (95% CI)", 
     ylab = "",
     yaxt = "n",
     main = "Forest Plot: Immediate vs. Delayed Feedback by Delay Category",
     cex.main = 1.2,
     bty = "n")

# Add vertical line at zero
abline(v = 0, lty = 2, col = "gray50", lwd = 1)

# Plot confidence intervals and points for individual studies
for (i in 1:n_rows) {
  if (!forest_data_final$is_pooled[i]) {
    # Individual study
    segments(
      x0 = forest_data_final$ci_lower[i],
      x1 = forest_data_final$ci_upper[i],
      y0 = y_positions[i],
      y1 = y_positions[i],
      lwd = 1,
      col = "gray30"
    )
    
    points(
      x = forest_data_final$hedges_g[i],
      y = y_positions[i],
      pch = 15,
      cex = 0.8,
      col = "gray30"
    )
  } else if (!is.na(forest_data_final$delay_category[i])) {
    # Subgroup pooled estimate
    segments(
      x0 = forest_data_final$ci_lower[i],
      x1 = forest_data_final$ci_upper[i],
      y0 = y_positions[i],
      y1 = y_positions[i],
      lwd = 3,
      col = "blue"
    )
    
    points(
      x = forest_data_final$hedges_g[i],
      y = y_positions[i],
      pch = 18,
      cex = 1.8,
      col = "blue"
    )
  } else {
    # Overall pooled estimate
    segments(
      x0 = forest_data_final$ci_lower[i],
      x1 = forest_data_final$ci_upper[i],
      y0 = y_positions[i],
      y1 = y_positions[i],
      lwd = 4,
      col = "red"
    )
    
    points(
      x = forest_data_final$hedges_g[i],
      y = y_positions[i],
      pch = 18,
      cex = 2.2,
      col = "red"
    )
  }
}

# Add study labels on the left
par(xpd = TRUE)
for (i in 1:n_rows) {
  label_text <- forest_data_final$study_label[i]
  font_style <- ifelse(forest_data_final$is_pooled[i], 2, 1)  # Bold for pooled
  cex_size <- ifelse(forest_data_final$is_pooled[i], 0.8, 0.7)
  
  text(
    x = x_min - 0.1 * (x_max - x_min),
    y = y_positions[i],
    labels = label_text,
    pos = 2,
    cex = cex_size,
    font = font_style
  )
  
  # Add effect size and CI on the right
  es_text <- sprintf("%.2f [%.2f, %.2f]", 
                     forest_data_final$hedges_g[i],
                     forest_data_final$ci_lower[i],
                     forest_data_final$ci_upper[i])
  
  text(
    x = x_max + 0.05 * (x_max - x_min),
    y = y_positions[i],
    labels = es_text,
    pos = 4,
    cex = cex_size,
    font = font_style
  )
}

# Add subgroup separators
for (cat_name in c("Short", "Intermediate", "Long")) {
  cat_rows <- which(forest_data_final$delay_category == cat_name)
  if (length(cat_rows) > 0) {
    max_row <- min(cat_rows)
    abline(h = y_positions[max_row] + 0.5, lty = 1, col = "gray70", lwd = 1)
  }
}

# Add final separator before overall
if (length(overall_row) > 0) {
  abline(h = y_positions[overall_row] + 0.5, lty = 1, col = "black", lwd = 2)
}

par(xpd = FALSE)

dev.off()

cat("Enhanced forest plot saved to:", file.path(file_path, "forest_plot_categorical_enhanced.pdf"), "\n")


# SAVE SUMMARY TO CSV (INCLUDING OVERALL)


write.csv(results_categorical, 
          file.path(file_path, "categorical_meta_analysis_results.csv"),
          row.names = FALSE)

cat("\nCategorical analysis results (including Overall) saved to CSV\n")

# ============================================================================
# FINAL SUMMARY
# ============================================================================

cat("\n\n" , "=== FINAL SUMMARY ===" , "\n")
cat("\nCategorical Meta-Analysis Complete!\n")
cat("\nFiles created:\n")
cat("  1. categorical_meta_analysis.tex - LaTeX table with pooled estimates (including Overall)\n")
cat("  2. categorical_meta_analysis_results.csv - Results in CSV format (including Overall)\n")
cat("  3. forest_plot_categorical.pdf - Forest plot using metafor\n")
cat("  4. forest_plot_categorical_enhanced.pdf - Enhanced forest plot\n")

cat("\n\nPooled Effect Sizes by Category (including Overall):\n")
print(results_categorical %>% select(Category, k, N, Estimate, CI_Lower, CI_Upper, p_value))
```
# 5- Forest Plots

## Goruped Forest Plot

```{r}

# COMPACT FOREST PLOT WITH CATEGORICAL SUBGROUPS - CUSTOMIZED


library(ggplot2)
library(dplyr)

cat("\n=== CREATING CUSTOMIZED CATEGORICAL FOREST PLOT ===\n")

# Prepare data: Keep all individual effects (not averaged)
forest_data_compact <- data_clean %>%
  mutate(
    ci_lower = hedges_g - 1.96 * se_g,
    ci_upper = hedges_g + 1.96 * se_g,
    type = "Individual Study",
    # Create a combined study-effect identifier for ordering
    study_effect = paste0("A_", unique_ID, "_", g_ID)  # Prefix with A_ for individual studies
  ) %>%
  select(unique_ID, g_ID, study_effect, delay_category, hedges_g, vi_g, se_g, ci_lower, ci_upper, type)

# Count effects and studies per category
category_counts <- data_clean %>%
  group_by(delay_category) %>%
  summarise(
    n_studies = n_distinct(unique_ID),
    n_effects = n(),
    .groups = "drop"
  )

print(category_counts)

# Add pooled estimates for each category (will be placed at the end)
# EXCLUDE "Not Reported" category from pooled estimates
pooled_by_category <- results_categorical %>%
  filter(Category != "Not Reported" & Category != "Overall") %>%  # Exclude Not Reported and Overall
  left_join(category_counts, by = c("Category" = "delay_category")) %>%
  mutate(
    unique_ID = paste0("POOLED_", Category),
    g_ID = "pooled",
    # Use Z_ prefix to ensure pooled effects sort to the END (Z comes after A)
    study_effect = paste0("Z_POOLED_", Category),
    hedges_g = Estimate,
    vi_g = SE^2,
    se_g = SE,
    ci_lower = CI_Lower,
    ci_upper = CI_Upper,
    delay_category = Category,
    type = "Subgroup Pooled",
    display_label = sprintf("%s (Pooled)", Category)  # Remove k and N here
  ) %>%
  select(unique_ID, g_ID, study_effect, delay_category, hedges_g, vi_g, se_g, ci_lower, ci_upper, type, display_label)

# Handle NA category (Not Reported) - NO POOLED EFFECT
na_data <- forest_data_compact %>%
  filter(is.na(delay_category)) %>%
  mutate(delay_category = "Not Reported")

# Get counts for NA category
if (nrow(na_data) > 0) {
  na_counts <- na_data %>%
    summarise(
      n_studies = n_distinct(unique_ID),
      n_effects = n()
    )
  
  # Update main data
  forest_data_compact <- forest_data_compact %>%
    mutate(delay_category = ifelse(is.na(delay_category), "Not Reported", delay_category))
}

# Add overall pooled estimate
overall_counts <- data_clean %>%
  summarise(
    n_studies = n_distinct(unique_ID),
    n_effects = n()
  )

overall_pooled_row <- tibble(
  unique_ID = "OVERALL_POOLED",
  g_ID = "overall",
  study_effect = "Z_OVERALL_POOLED",
  delay_category = "Overall",
  hedges_g = g_feedback_time_corr_without_outliers$reg_table$b.r,
  vi_g = g_feedback_time_corr_without_outliers$reg_table$SE^2,
  se_g = g_feedback_time_corr_without_outliers$reg_table$SE,
  ci_lower = g_feedback_time_corr_without_outliers$reg_table$CI.L,
  ci_upper = g_feedback_time_corr_without_outliers$reg_table$CI.U,
  type = "Overall Pooled",
  display_label = "Overall (Pooled)"  # Remove k and N here since they're in the facet label
)

# Combine all data
forest_plot_data <- bind_rows(
  forest_data_compact,
  pooled_by_category,
  overall_pooled_row
) %>%
  mutate(
    # Create display labels for individual studies
    display_label = ifelse(
      type == "Individual Study",
      paste0(unique_ID, " (", g_ID, ")"),
      display_label
    ),
    delay_category = factor(
      delay_category, 
      levels = c("Short", "Intermediate", "Long", "Not Reported", "Overall")
    ),
    type = factor(type, levels = c("Individual Study", "Subgroup Pooled", "Overall Pooled"))
  ) %>%
  # Sort to ensure within each category: Individual Studies first, then Pooled
  arrange(delay_category, type, unique_ID, g_ID) %>%
  # Reverse the order within each category so pooled appears at bottom visually
  group_by(delay_category) %>%
  mutate(plot_order = rev(row_number())) %>%
  ungroup()

# Add category labels with counts for facet strips (k and N in italic using expression)
category_labels <- category_counts %>%
  mutate(
    label = sprintf("%s~'('*italic(k)*'='*%d*','~italic(N)*'='*%d*')'", 
                   delay_category, 
                   n_effects, 
                   n_studies)
  )

# Add NA category label if exists
if (exists("na_counts")) {
  na_label <- tibble(
    delay_category = "Not Reported",
    label = sprintf("'Not Reported'~'('*italic(k)*'='*%d*','~italic(N)*'='*%d*')'", na_counts$n_effects, na_counts$n_studies)
  )
  category_labels <- bind_rows(category_labels, na_label)
}

# Add overall label
overall_label <- tibble(
  delay_category = "Overall",
  label = sprintf("Overall~'('*italic(k)*'='*%d*','~italic(N)*'='*%d*')'", overall_counts$n_effects, overall_counts$n_studies)
)
category_labels <- bind_rows(category_labels, overall_label)

# Create named vector for facet labels
facet_labels <- setNames(
  category_labels$label,
  category_labels$delay_category
)

cat("\nForest plot data prepared:\n")
cat("  Total rows:", nrow(forest_plot_data), "\n")
cat("  Individual effects:", sum(forest_plot_data$type == "Individual Study"), "\n")
cat("  Subgroup pooled:", sum(forest_plot_data$type == "Subgroup Pooled"), "\n")
cat("  Overall pooled: 1\n")


# CREATE THE FOREST PLOT


# Create color palette
colors <- c("Individual Study" = "gray40", 
            "Subgroup Pooled" = "#2E86AB", 
            "Overall Pooled" = "#A23B72")

# Create shapes
shapes <- c("Individual Study" = 16,  # circle
            "Subgroup Pooled" = 18,  # diamond
            "Overall Pooled" = 18)   # diamond

# Create sizes
sizes <- c("Individual Study" = 2, 
           "Subgroup Pooled" = 4, 
           "Overall Pooled" = 5)

# Create the forest plot with LARGER FONT SIZES FOR EVERYTHING
p_forest <- ggplot(forest_plot_data, 
                   aes(x = hedges_g, 
                       y = reorder(display_label, plot_order),  # Use plot_order for correct sequence
                       color = type,
                       shape = type,
                       size = type)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), 
                 height = 0.2, 
                 linewidth = 0.5,
                 alpha = 0.7) +
  geom_point() +
  scale_color_manual(values = colors, name = "Estimate Type") +
  scale_shape_manual(values = shapes, name = "Estimate Type") +
  scale_size_manual(values = sizes, name = "Estimate Type") +
  facet_grid(delay_category ~ ., 
             scales = "free_y", 
             space = "free_y", 
             switch = "y",
             labeller = labeller(delay_category = as_labeller(facet_labels, default = label_parsed))) +
  labs(
    x = "Hedges' g (95% CI)",
    y = "Delayed Feedback Delay"
  ) +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(angle = 0, hjust = 1, face = "bold", size = 14),  # Category labels - slightly smaller
    strip.placement = "outside",
    panel.spacing = unit(1.2, "lines"),  # More spacing between subgroups
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(size = 13),  # Legend - LARGER
    axis.text.y = element_text(size = 13),  # STUDY NAMES - LARGER
    axis.text.x = element_text(size = 13),  # X-axis ticks - LARGER
    axis.title.x = element_text(size = 15, face = "bold"),  # "Hedges' g" - LARGER
    axis.title.y = element_text(size = 15, face = "bold"),  # "Delayed Feedback Delay" - LARGER
    plot.title = element_blank()
  )

# Save the plot
ggsave(
  filename = file.path(file_path, "forest_plot_compact_custom.pdf"),
  plot = p_forest,
  width = 10,
  height = max(8, nrow(forest_plot_data) * 0.15),
  device = "pdf"
)

ggsave(
  filename = file.path(file_path, "forest_plot_compact_custom.png"),
  plot = p_forest,
  width = 10,
  height = max(8, nrow(forest_plot_data) * 0.15),
  dpi = 300
)

cat("\nCustomized forest plot saved:\n")
cat("  PDF:", file.path(file_path, "forest_plot_compact_custom.pdf"), "\n")
cat("  PNG:", file.path(file_path, "forest_plot_compact_custom.png"), "\n")

# Display the plot
print(p_forest)


# MINI VERSION (More Compact) - WITH LARGER FONTS AND MORE SPACING


# Create shorter labels
forest_plot_data_mini <- forest_plot_data %>%
  mutate(
    display_label_short = case_when(
      type == "Overall Pooled" ~ display_label,
      type == "Subgroup Pooled" ~ gsub("\\(Pooled.*", "(Pooled)", display_label),
      TRUE ~ gsub(" \\(es_[0-9]+\\)", "", display_label)  # Remove effect IDs for cleaner look
    )
  )

p_forest_mini <- ggplot(forest_plot_data_mini, 
                        aes(x = hedges_g, 
                            y = reorder(display_label_short, plot_order),  # Use plot_order for correct sequence
                            color = type,
                            shape = type,
                            size = type)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), 
                 height = 0.15, 
                 linewidth = 0.4,
                 alpha = 0.7) +
  geom_point() +
  scale_color_manual(values = colors, name = "") +
  scale_shape_manual(values = shapes, name = "") +
  scale_size_manual(values = sizes, name = "") +
  facet_grid(delay_category ~ ., 
             scales = "free_y", 
             space = "free_y", 
             switch = "y",
             labeller = labeller(delay_category = as_labeller(facet_labels, default = label_parsed))) +
  labs(
    x = "Hedges' g (95% CI)",
    y = "Delayed Feedback Delay"
  ) +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(angle = 0, hjust = 1, face = "bold", size = 13),  # Category labels - slightly smaller
    strip.placement = "outside",
    panel.spacing = unit(1.5, "lines"),  # MORE SPACING between subgroups
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(size = 12),  # Legend - LARGER
    axis.text.y = element_text(size = 12),  # STUDY NAMES - LARGER
    axis.text.x = element_text(size = 12),  # X-axis ticks - LARGER
    axis.title.x = element_text(size = 14, face = "bold"),  # "Hedges' g" - LARGER
    axis.title.y = element_text(size = 14, face = "bold"),  # "Delayed Feedback Delay" - LARGER
    plot.title = element_blank()
  )

# Save mini version
ggsave(
  filename = file.path(file_path, "forest_plot_mini_custom.pdf"),
  plot = p_forest_mini,
  width = 12,
  height = max(6, nrow(forest_plot_data) * 0.12),
  device = "pdf"
)

ggsave(
  filename = file.path(file_path, "forest_plot_mini_custom.png"),
  plot = p_forest_mini,
  width = 12,
  height = max(6, nrow(forest_plot_data) * 0.12),
  dpi = 300
)

cat("\nMini customized forest plot saved:\n")
cat("  PDF:", file.path(file_path, "forest_plot_mini_custom.pdf"), "\n")
cat("  PNG:", file.path(file_path, "forest_plot_mini_custom.png"), "\n")

print(p_forest_mini)


# INTERACTIVE VERSION


library(plotly)

# Create hover text
forest_plot_data <- forest_plot_data %>%
  mutate(
    hover_text = paste0(
      "Study: ", unique_ID, "<br>",
      "Effect: ", g_ID, "<br>",
      "Category: ", delay_category, "<br>",
      "Hedges' g: ", round(hedges_g, 3), "<br>",
      "95% CI: [", round(ci_lower, 3), ", ", round(ci_upper, 3), "]", "<br>",
      "Type: ", type
    )
  )

# Convert to plotly (using mini version for better display)
p_interactive <- ggplotly(p_forest_mini, tooltip = "text") %>%
  layout(
    autosize = TRUE,
    height = max(600, nrow(forest_plot_data) * 15),
    hovermode = "closest"
  )

# Save as HTML
htmlwidgets::saveWidget(
  p_interactive,
  file.path(file_path, "forest_plot_interactive_custom.html"),
  selfcontained = TRUE
)

cat("\nInteractive forest plot saved:", file.path(file_path, "forest_plot_interactive_custom.html"), "\n")


# SUMMARY


cat("\n\n=== CUSTOMIZED FOREST PLOTS CREATED ===\n")
cat("\nAll requested changes implemented:\n")
cat("  ✓ Multiple effects from same study plotted separately\n")
cat("  ✓ Subgroup pooled effects at the END of each group (A_ vs Z_ prefix)\n")
cat("  ✓ 'Not Reported' category added (NO pooled effect)\n")
cat("  ✓ No plot title\n")
cat("  ✓ Y-axis labeled as 'Delayed Feedback Delay'\n")
cat("  ✓ Category labels include k (effects) and N (studies)\n")
cat("  ✓ LARGER font sizes for ALL text (categories, axis titles, study names)\n")
cat("  ✓ Increased spacing between subgroups\n")

cat("\n\nFiles created:\n")
cat("  1. forest_plot_compact_custom.pdf/.png - Main version\n")
cat("  2. forest_plot_mini_custom.pdf/.png - Compact version\n")
cat("  3. forest_plot_interactive_custom.html - Interactive version\n")
```


```{r}

# MINI VERSION (More Compact) - WITH LARGER FONTS AND MORE SPACING


# Create shorter labels
forest_plot_data_mini <- forest_plot_data %>%
  mutate(
    display_label_short = case_when(
      type == "Overall Pooled" ~ display_label,
      type == "Subgroup Pooled" ~ gsub("\\(Pooled.*", "(Pooled)", display_label),
      TRUE ~ gsub(" \\(es_[0-9]+\\)", "", display_label)  # Remove effect IDs for cleaner look
    )
  )

# Get data for the Overall category only
overall_data <- forest_plot_data_mini %>%
  filter(delay_category == "Overall")

p_forest_mini <- ggplot(forest_plot_data_mini, 
                        aes(x = hedges_g, 
                            y = reorder(display_label_short, plot_order),  # Use plot_order for correct sequence
                            color = type,
                            shape = type,
                            size = type)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), 
                 height = 0.15, 
                 linewidth = 0.4,
                 alpha = 0.7) +
  geom_point() +
  # Add arrows only for Overall category
  geom_segment(data = overall_data,
               aes(x = 0, y = 0.5, 
                   xend = 2, 
                   yend = 0.5), 
               arrow = arrow(length = unit(0.2, "cm")), color = "#893F45",linewidth = 0.3) +
  geom_segment(data = overall_data,
               aes(x = 0, y = 0.5, 
                   xend = -2, 
                   yend = 0.5), 
               arrow = arrow(length = unit(0.2, "cm")), color = "#893F45",linewidth = 0.3) +
  # Add text labels only for Overall category
  geom_text(data = overall_data,
            aes(x = max(forest_plot_data_mini$hedges_g, na.rm = TRUE) , 
                y = 1),
            label = "Favours immediate feedback", hjust = 0.5, color = "#893F45", size = 4,
            inherit.aes = FALSE) +
  geom_text(data = overall_data,
            aes(x = min(forest_plot_data_mini$hedges_g, na.rm = TRUE) , 
                y = 1),
            label = "Favours delayed feedback", hjust = 0.5, color = "#893F45", size = 4,
            inherit.aes = FALSE) +
  scale_color_manual(values = colors, name = "") +
  scale_shape_manual(values = shapes, name = "") +
  scale_size_manual(values = sizes, name = "") +
  facet_grid(delay_category ~ ., 
             scales = "free_y", 
             space = "free_y", 
             switch = "y",
             labeller = labeller(delay_category = as_labeller(facet_labels, default = label_parsed))) +
  labs(
    x = "Hedges' g (95% CI)",
    y = "Delayed Feedback Delay"
  ) +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(angle = 0, hjust = 1, face = "bold", size = 13),
    strip.placement = "outside",
    panel.spacing = unit(1.5, "lines"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
    legend.text = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.title.x = element_text(size = 14, face = "bold"),
    axis.title.y = element_text(size = 14, face = "bold"),
    plot.title = element_blank()
  )

# Save mini version
ggsave(
  filename = file.path(file_path, "forest_plot_mini_custom.pdf"),
  plot = p_forest_mini,
  width = 12,
  height = max(6, nrow(forest_plot_data) * 0.12),
  device = "pdf"
)

ggsave(
  filename = file.path(file_path, "forest_plot_mini_custom.png"),
  plot = p_forest_mini,
  width = 12,
  height = max(6, nrow(forest_plot_data) * 0.12),
  dpi = 300
)

cat("\nMini customized forest plot saved:\n")
cat("  PDF:", file.path(file_path, "forest_plot_mini_custom.pdf"), "\n")
cat("  PNG:", file.path(file_path, "forest_plot_mini_custom.png"), "\n")

print(p_forest_mini)
```


## Big Forest Plot
```{r}
# Load necessary libraries
library(htmltools)   # For saving HTML files
library(webshot)     # For saving plots as images (optional, but recommended)
library(knitr)       # For including images in HTML
library(magrittr)    # For using the %>% pipe operator

# Save the forest plot as a PNG file
png(filename = "forest_plot.png", width = 8.5, height = 56, units = "in", res = 300) # APA7 paper size
forest.robu(
  g_feedback_time_corr_without_outliers, 
  es.lab = "experiment_number", 
  study.lab = "unique_ID", 
  "Weight" = r.weights, 
  "Effect Size" = hedges_g
)
dev.off()  # Close the image file

# Create an HTML file and embed the image
html_file <- htmltools::tagList(
  tags$html(
    tags$head(tags$title("")),
    tags$body(
      h1(""),
      tags$img(src = "forest_plot.png", width = "100%") # Embed the PNG image
    )
  )
)

# Save the HTML file
htmltools::save_html(html_file, file = "forest_plot.html")

```
## interactive forest plot

```{r}
library(ggplot2)
library(plotly)

# Assuming data_clean is already prepared with the necessary columns
# Create ggplot object for the forest plot
forest_plot <- ggplot(data_clean, aes(x = hedges_g, y = reorder(unique_ID, hedges_g))) +
  geom_point() +
  geom_errorbarh(aes(xmin = hedges_g - 1.96 * sqrt(vi_g), xmax = hedges_g + 1.96 * sqrt(vi_g)), height = 0.1)

# Convert the ggplot object to a plotly object and specify dimensions
interactive_forest_plot <- ggplotly(forest_plot) %>%
  layout(
    title = "",
    xaxis = list(title = "Effect Size (Hedges' g)"),
    yaxis = list(title = "Study ID"),
    autosize = FALSE,
    width = 1000,   # Width in pixels
    height = 1200,    # Height in pixels
       plot_bgcolor = 'rgba(0,0,0,0)',  # Transparent plot background
    paper_bgcolor = 'rgba(0,0,0,0)'  # Transparent paper background
  )

# Render the plot
interactive_forest_plot

```


# 6- Publication Bias

ss## 6.1- funnel plot before trimfill
```{r}
result_model= g_feedback_time_corr_without_outliers$reg_table
## define estimate and se
estimate = result_model$b.r
se = result_model$SE

#Store a vector of values that spans the range from 0 to the max value of impression (standard error) in your dataset.
#Make the increment (the final value) small enough (I choose 0.001) to ensure your whole range of data is captured
se.seq=seq(0, max(data_clean$se_g), 0.001)

#Compute vectors of the lower-limit and upper limit values for
#the 95% CI region
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)

#Do this for a 99% CI region too
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)

#And finally, calculate the confidence interval for your meta-analytic estimate 
# directly capture from the RVE model
meanll95 = result_model$CI.L
meanul95 = result_model$CI.U

#Put all calculated values into one data frame
#You might get a warning about '...row names were found from a short variable...' 
#You can ignore it.
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)

#Draw Plot
library(ggplot2)
fp_fixD = ggplot(aes(x = se_g, y = hedges_g), data = data_clean) +
  geom_point(shape = 1) +
  xlab('Standard Error') + ylab('Effect sizes (Hedges g)') + 
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='solid', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='solid', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = estimate, xend = max(se.seq), yend = estimate), linetype='solid', colour ="red", data=dfCI) +
  scale_x_reverse() +
  scale_y_continuous(breaks=seq(-12.5,2.50,0.50))+
  coord_flip()+
  theme_classic() +
  plot_theme

fp_fixD 

ggsave("funnel_before_correction.png", plot = fp_fixD, width = 10, height = 8, dpi = 300)

```

## 6.2- Eggers Test

```{r}
# Prepare the data frame required by eggers test
data_for_eggers_test <- data.frame(
  effect_size = g_feedback_time_corr_without_outliers$data.full$effect.size,
  std_error = sqrt(g_feedback_time_corr_without_outliers$data.full$var.eff.size),
  variance=g_feedback_time_corr_without_outliers$data.full$var.eff.size
)

eggers_test <- data_for_eggers_test %>% 
  mutate(y = effect_size/sqrt(variance), x = 1/sqrt(variance)) %>% 
  lm(y ~ x, data = .) 

eggers_test

# Constructing the unified result table
result_egger <- tibble(
  Statistic = c(
    "Intercept", "Inverse SE", 
    "Num. Obs.", "R²", "Adjusted R²", "AIC", "BIC", "Log Likelihood", "RMSE"
  ),
  Estimate = round(c(
    coef(summary(eggers_test))[1, 1], coef(summary(eggers_test))[2, 1], 
    nobs(eggers_test), 
    summary(eggers_test)$r.squared, summary(eggers_test)$adj.r.squared,
    AIC(eggers_test), BIC(eggers_test), as.numeric(logLik(eggers_test)), sigma(eggers_test)
  ), 2),
  `Std. Error` = c(
    round(coef(summary(eggers_test))[1, 2], 2), round(coef(summary(eggers_test))[2, 2], 2), 
    "", "","","","","",""
  ),
  `t Statistic` = c(
    sprintf("t = %.2f", coef(summary(eggers_test))[1, 3]), sprintf("t = %.2f", coef(summary(eggers_test))[2, 3]),
    "", "","","","","",""
  ),
  `P value` = c(
    ifelse(coef(summary(eggers_test))[1, 4] < 0.001, "p < 0.001", sprintf("p = %.3f", coef(summary(eggers_test))[1, 4])),
    ifelse(coef(summary(eggers_test))[2, 4] < 0.001, "p < 0.001", sprintf("p = %.3f", coef(summary(eggers_test))[2, 4])),
    "", "","","","","",""
  )
)

# Create the LaTeX table using kableExtra with a horizontal line after the "Inverse SE"
latex_table <- result_egger %>%
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "lllll",  # Alignment for each column
    col.names = c("Statistic", "Estimate", "Std. Error", "t Statistic", "P value")
  ) %>%
  kable_styling(
    latex_options = c("hold_position"),
    full_width = FALSE
  ) %>%
  add_header_above(c(" " = 1, "Egger's Regression Test" = 4)) %>%
  row_spec(
    2, # The row right after 'Inverse SE', which is the third row (index is 0-based in row_spec)
    extra_latex_after = "\\midrule"
  ) %>%
  footnote(
    general = "Results of Egger's regression test. No adjustments have been made.",
    threeparttable = TRUE
  )

   # Write the LaTeX table to a .tex file
    tex_filename <- normalizePath(file.path(file_path, "table_eggers_test.tex"), mustWork = FALSE)
    
    tryCatch({
      cat(latex_table, file = tex_filename)
      if (file.exists(tex_filename)) {
        message("File successfully created: ", tex_filename)
      } else {
        warning("Failed to create file: ", tex_filename)
      }
    }, error = function(e) {
      warning("An error occurred while writing file for moderator '", moderator, "': ", e$message)
    })
  

# Print the LaTeX table
cat(latex_table)

```


## 6.3- Funnel Plot after trimfill 

### funnel with directions

```{r}
result_model= g_feedback_time_corr_without_outliers$reg_table
## define estimate and se
estimate = result_model$b.r
se = result_model$SE
#Store a vector of values that spans the range from 0 to the max value of impression (standard error) in your dataset.
#Make the increment (the final value) small enough (I choose 0.001) to ensure your whole range of data is captured
se.seq=seq(0, max(data_clean$se_g), 0.001)
#Compute vectors of the lower-limit and upper limit values for
#the 95% CI region
ll95 = estimate-(1.96*se.seq)
ul95 = estimate+(1.96*se.seq)
#Do this for a 99% CI region too
ll99 = estimate-(3.29*se.seq)
ul99 = estimate+(3.29*se.seq)
#And finally, calculate the confidence interval for your meta-analytic estimate 
# directly capture from the RVE model
meanll95 = result_model$CI.L
meanul95 = result_model$CI.U
#Put all calculated values into one data frame
#You might get a warning about '...row names were found from a short variable...' 
#You can ignore it.
dfCI = data.frame(ll95, ul95, ll99, ul99, se.seq, estimate, meanll95, meanul95)
#Draw Plot
library(ggplot2)
fp_fixD = ggplot(aes(x = se_g, y = hedges_g), data = data_clean) +
  geom_point(shape = 1) +
 xlab('Standard Error') + ylab("Hedges' g") +
  geom_line(aes(x = se.seq, y = ll95), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul95), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ll99), linetype = 'dashed', data = dfCI) +
  geom_line(aes(x = se.seq, y = ul99), linetype = 'dashed', data = dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanll95, xend = max(se.seq), yend = meanll95), linetype='solid', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = meanul95, xend = max(se.seq), yend = meanul95), linetype='solid', data=dfCI) +
  geom_segment(aes(x = min(se.seq), y = estimate, xend = max(se.seq), yend = estimate), linetype='solid', colour ="red", data=dfCI) +
  # Add arrows pointing outward from center (y=0)
  geom_segment(aes(x = min(se.seq), y = 0, xend = min(se.seq), yend = max(data_clean$hedges_g, na.rm = TRUE)), 
               arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
  geom_segment(aes(x = min(se.seq), y = 0, xend = min(se.seq), yend = min(data_clean$hedges_g, na.rm = TRUE)), 
               arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
  # Add text labels
  annotate("text", x = min(se.seq) - 0.02, y = max(data_clean$hedges_g, na.rm = TRUE) / 2, 
           label = "Favours immediate feedback", hjust = 0.5, color = "#893F45", size = 6) +
  annotate("text", x = min(se.seq) - 0.02, y = min(data_clean$hedges_g, na.rm = TRUE) / 2, 
           label = "Favours delayed feedback", hjust = 0.5, color = "#893F45", size = 6) +
  scale_x_reverse() +
  scale_y_continuous(breaks=seq(-12.5,2.50,0.50))+
  coord_flip()+
  theme_classic() +
  plot_theme
fp_fixD 
ggsave("fig_funnel_before_correction.png", plot = fp_fixD, width = 10, height = 8, dpi = 300)
```

# 7- Moderators

## 7.1- Moderator Plots

### 7.1.a- Function: moderator plots
```{r}
moderator_plots <- function(data_input, name, threshold_for_moderator = threshold_for_moderator, moderators_list = NULL, common_plot = TRUE, remove_small_groups = TRUE) {
  
  # Use the provided moderators list or default list
  if (is.null(moderators_list)) {
    moderators <- c(
      "feedback_type_simple_elaborated", 
      "delay_definition", 
      "feedback_delay_difference_converted_to_time_log",
      "educational_level_tertiary_others",  
      "learning_domain", 
      "task_level", 
      "prior_knowledge", 
      "experimental_vs_curriculum_based_task"
    )
  } else {
    moderators <- moderators_list
  }
  
  # Empty list to store plots
  plot_list <- list()
  
  for (moderator in moderators) {
    
    data=data_input
    
    plot <- NULL
    
    # Calculate if the current moderator is continuous
    is_continuous <- is.numeric(data[[moderator]]) && !is.factor(data[[moderator]])
    message("Processing moderator: ", moderator, " | is_continuous: ", is_continuous)
    
    adjusted_color_palette <- color_blind_friendly_palette
    
    # Count total NAs for the current moderator before filtering small groups
    total_na_count <- sum(is.na(data[[moderator]]))
    
    # Check if the moderator is continuous
    #is_continuous <- is.numeric(data[[moderator]]) || n_distinct(data[[moderator]]) > 15
    
    if (!is_continuous && remove_small_groups) {
      # Count occurrences of each unique value in the moderator
      small_groups <- data %>%
        count(.data[[moderator]]) %>%
        filter(n < threshold_for_moderator) %>%
        pull(.data[[moderator]])  # Extract the names of small categories

      # Record original levels of the moderator before filtering
      original_levels <- levels(factor(data[[moderator]]))

      # Replace small groups with NA
      data <- data %>%
        mutate(across(all_of(moderator), ~ ifelse(. %in% small_groups, NA, .)))
      
      # Get remaining levels of the moderator after filtering
      remaining_levels <- levels(factor(data[[moderator]]))
      
      # Get indices of the removed categories
      removed_indices <- which(!(original_levels %in% remaining_levels))
      
      if (length(removed_indices) > 0) {
  adjusted_color_palette <- color_blind_friendly_palette[-removed_indices]
}
      
    }
    
    # Drop NA values for the moderator
    plot_data <- data %>%
      mutate(across(all_of(moderator), ~ factor(.))) %>%  
      drop_na(.data[[moderator]])
    
    # Replace underscores with spaces in the moderator's levels
plot_data <- plot_data %>%
  mutate(across(all_of(moderator), ~ gsub("_", " ", .)))
    
    # Skip plotting if no data left
    if (nrow(plot_data) == 0) {
      next
    }
    
    if (is_continuous) {
      # Ensure moderator is numeric for continuous plots
      plot_data[[moderator]] <- as.numeric(plot_data[[moderator]])
      
      # Check if variance of hedges_g is 0, skip if no variance
      if (var(plot_data$hedges_g, na.rm = TRUE) == 0) {
        next
      }
      
      min_y <- if (is.numeric(plot_data[[moderator]])) min(plot_data[[moderator]], na.rm = TRUE) else NA

          
      # Calculate total number of points for annotation
      n_points <- nrow(plot_data)
      
      # Plot for continuous moderator
      plot <- ggplot(plot_data, aes(x = hedges_g, y = .data[[moderator]])) +
        geom_point(aes(color = se_g), alpha = 0.6) +
        tryCatch({
          geom_smooth(method = "lm", se = TRUE, color = "darkred")
        }, error = function(e) {
          message("Error in geom_smooth for moderator: ", moderator)
          return(NULL)
        }) +
        # Add annotation with total number of points and total NAs
        annotate("text", x = max(plot_data$hedges_g, na.rm = TRUE), 
                 y = min_y, 
                 label = paste0("n = ", n_points, 
                                if (total_na_count > 0) paste0("\nNA = ", total_na_count) else ""), 
                 hjust = 1, vjust = -0.5, 
                 color = "#525252", 
                 fontface = "bold", 
                 size = 4) +
         labs(x = paste0("Hedge's g (", name, ")"), y = gsub("_", " ", moderator)) +
                geom_segment(aes(x = 0, y = min_y - 0.5, 
                         xend = max(plot_data$hedges_g, na.rm = TRUE), yend = min_y - 0.5), 
                     arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
        geom_segment(aes(x = 0, y = min_y - 0.5, 
                         xend = min(plot_data$hedges_g, na.rm = TRUE), yend = min_y - 0.5), 
                     arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
        annotate("text", x = max(plot_data$hedges_g, na.rm = TRUE) / 2, 
                 y = min_y - 1, 
                 label = "Immediate Feedback", hjust = 0.5, color = "#893F45") +
        annotate("text", x = min(plot_data$hedges_g, na.rm = TRUE) / 2, 
                 y = min(plot_data[[moderator]], na.rm = TRUE) - 1, 
                 label = "Delayed Feedback", hjust = 0.5, color = "#893F45")+  
        plot_theme + 
        theme(
          axis.title = element_text(size = rel(0.8), face = "plain"),
          panel.grid.major.x = element_line(color = "#F0F0F0", size = 0.5), 
          panel.grid.minor.x = element_line(color = "#F0F0F0", size = 0.25)
        )
      
    } else {
      # Calculate number of points in each category
      n_points_per_group <- plot_data %>%
        count(.data[[moderator]]) %>%
        rename(n = n)
      
       # Plot for categorical moderator
  plot <- ggplot(plot_data, aes(x = .data[[moderator]], y = hedges_g)) +
    geom_half_boxplot(aes(color = .data[[moderator]], group = .data[[moderator]]), 
                      side = "l", size = 0.5, nudge = 0.05, 
                      outlier.shape = NA, alpha = 0.7) +
    geom_half_violin(aes(fill = .data[[moderator]], group = .data[[moderator]]), 
                     side = "r", nudge = 0.05, 
                     alpha = 0.7) +
    geom_half_point(aes(color = .data[[moderator]], group = .data[[moderator]]), 
                    side = "l", 
                    position = position_jitter(width = 0.1, height = 0),
                    alpha = 0.7) +
    geom_hline(yintercept = 0, 
               linewidth = 0.5, linetype = "24", color = "grey") +
    # Horizontal arrows from center
    geom_segment(aes(x = 0.55, y = 0, xend = 0.55, yend = -1.5), 
                 arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
    geom_segment(aes(x = 0.55, y = 0, xend = 0.55, yend = 1.5), 
                 arrow = arrow(length = unit(0.2, "cm")), color = "#893F45") +
    # Labels for arrows, repositioned for clarity
    annotate("text", x = 0.5, y = -0.5, label = "Delayed Feedback", hjust = 0.5, color = "#893F45") +
    annotate("text", x = 0.5, y = 0.5, label = "Immediate Feedback", hjust = 0.5, color = "#893F45") +
    # Annotate the number of points for each group
    geom_text(data = n_points_per_group, 
              aes(x = .data[[moderator]], 
                  y = max(plot_data$hedges_g, na.rm = TRUE) + 0.3, 
                  label = paste0("n = ", n)), 
              vjust = -0.5, 
              color = "#525252", 
              fontface = "bold", 
              size = 4) +
    scale_color_manual(values = adjusted_color_palette) +
    scale_fill_manual(values = adjusted_color_palette) +
    guides(color = "none", fill = "none") +
    labs(x = NULL, y = paste0("Hedge's g (", name, ")")) +
    plot_theme + 
    theme(
      axis.title = element_text(size = rel(0.8), face = "plain"),
      panel.grid.major.x = element_line(color = "#F0F0F0", size = 0.5), 
      panel.grid.minor.x = element_line(color = "#F0F0F0", size = 0.25)
    ) +
    coord_flip()
    }
    
    plot_list[[moderator]] <- plot
    
    
  }
  
    if (common_plot == TRUE) {
      plot <- ggpubr::ggarrange(
        plotlist = plot_list,
        labels = gsub("_", " ", moderators),
        font.label = list(size = 10), 
        ncol = 2, 
        nrow = 4
      ) %>%
      ggpubr::annotate_figure(
        top = ggpubr::text_grob(name, face = "bold", size = 12)
      )
      
      ggsave(filename = paste0(name, "_combined_plot.png"), plot = plot, width = 12, height = 10)
      return(plot)
    } else {
      names(plot_list) <- moderators
      for (i in seq_along(plot_list)) {
        ggsave(filename = paste0(name, "_", moderators[i], ".png"), plot = plot_list[[i]], width = 8, height = 6)
      }
      return(plot_list) 
    }
  
  
}

```


### 7.1.b- moderator plots for all moderators
```{r}
  # Define moderators
  moderators <- c('feedback_type', 'feedback_type_mixed_grouped', 'delay_definition','feedback_delay_difference','educational_level','learning_domain', 
                    'task_level', 'experimental_vs_curriculum_based_task','participant_design', 'arbitrary_learning','item_posttest', 
                    'delayed_feedback_given_in', 'retention_interval', 'feedback_provided', 'feedback_remind_answer', 'nb_item_in_training', 
                    'posttest_category', 'learning_material_type_in_training','memory_retrieval_vs_knowledge_application', 
                    'feedback_type_kr_kcr_ef_tryagain', 'feedback_type_simple_elaborated','year','time_limit_for_answer', 'time_limit_for_answer_include_not_reported',
                    'feedback_i_d_rate','interval_btw_last_feedback_and_posttest_controlled', 'prior_knowledge','feedback_delay_difference_converted_to_time_log', 'retention_interval_difference_btw_lastfeedback_posttest'
   
  )


# select the columns and rename 
for_moderator_plots <- data_clean %>%
  select(
    hedges_g,
    se_g,
    feedback_type_simple_elaborated, 
    delay_definition, 
    feedback_delay_difference_converted_to_time_log,
    educational_level,  
    learning_domain, 
    task_level, 
    prior_knowledge, 
    experimental_vs_curriculum_based_task
  ) %>%
  rename(
    feedback_type = feedback_type_simple_elaborated,
    delay_difference = feedback_delay_difference_converted_to_time_log,
    experimental_vs_curriculum_task = experimental_vs_curriculum_based_task
  )
   
preregistered_moderators_plot_list= c(
  "feedback_type", 
  "delay_definition", 
  "delay_difference",
  "educational_level",  
  "learning_domain", 
  "task_level", 
  "prior_knowledge", 
  "experimental_vs_curriculum_task"
)

for_moderator_plots_exploratory <- data_clean %>%
  select(hedges_g,
    se_g,
    participant_design,
    arbitrary_learning,
    item_posttest, 
    feedback_provided, 
    feedback_remind_answer, 
    nb_item_in_training, 
    memory_retrieval_vs_knowledge_application,
    year, 
    time_limit_for_answer_include_not_reported,
    retention_interval_difference_btw_lastfeedback_posttest) %>%
  rename(
    learning_type = arbitrary_learning,
    posttest_item = item_posttest,
    nb_training_item = nb_item_in_training,
    posttest_task=memory_retrieval_vs_knowledge_application,
    publication_year=year,
    answer_time=time_limit_for_answer_include_not_reported,
    retention_interval=retention_interval_difference_btw_lastfeedback_posttest
  )

exploratory_moderators_plot_list= c(
  "participant_design", 
  "learning_type", 
  "posttest_item",
  "feedback_provided",  
  "feedback_remind_answer", 
  "nb_training_item", 
  "posttest_task", 
  "publication_year",
  "answer_time",
  "retention_interval"
)

```



### Function: Moderators Model

```{r}
calculate_moderator_models <- function(input_data, moderators, list_report = FALSE, file_path = getwd(), all_together = FALSE, threshold_for_moderator = 5, remove_small_groups = TRUE) {
  
  # Normalize and create the file path if it does not exist
  file_path <- normalizePath(file_path, mustWork = FALSE)
  
  if (!dir.exists(file_path)) {
    dir.create(file_path, recursive = TRUE)
    message("Directory created: ", file_path)
  }
  
  message("Saving .tex files to: ", file_path)
  message("Current working directory: ", getwd())
  
  moderator_models <- list()
  references <- list()  # Store reference info for each moderator

  # Loop through each moderator and create models
  for (moderator in moderators) {
    
    data <- input_data
    
    if (!moderator %in% colnames(data)) {
      warning("Moderator '", moderator, "' not found in the data. Skipping this moderator.")
      next
    }
    
    # Convert character variables to factors
    if (is.character(data[[moderator]])) {
      data[[moderator]] <- as.factor(data[[moderator]])
      message("Converted moderator '", moderator, "' from character to factor.")
    }
    
    # Remove small groups for categorical moderators
    if (remove_small_groups && is.factor(data[[moderator]])) {
      small_groups <- data %>%
        count(.data[[moderator]], name = "n") %>%
        filter(n < threshold_for_moderator) %>%
        pull(.data[[moderator]])
      
      if (!is.null(small_groups) && length(small_groups) > 0) {
        # Replace small groups with NA while preserving factor levels
        data[[moderator]][data[[moderator]] %in% small_groups] <- NA
        data[[moderator]] <- forcats::fct_drop(data[[moderator]])  # Drop unused levels
        message("Removed small groups from moderator '", moderator, "'.")
      }
    }
    
    # Drop NA values only for categorical moderators
    if (!is.numeric(data[[moderator]])) {
      data <- data %>%
        drop_na(.data[[moderator]])
    }
    
    # Calculate the reference category for this moderator after cleaning
    reference <- if (is.factor(data[[moderator]])) {
      levels(droplevels(data[[moderator]]))[1]  # Get first valid level after cleaning
    } else {
      NULL
    }
    
    # Store the reference for this moderator
    references[[moderator]] <- reference
    
    # Fit the model
    tryCatch({
      model <- robu(formula = as.formula(paste0("hedges_g ~ ", moderator)), data = data, 
                    studynum = unique_ID, var.eff.size = vi_g, 
                    rho = rho, modelweights = "HIER", small = FALSE)
      moderator_models[[moderator]] <- model
    }, error = function(e) {
      warning("An error occurred while fitting model for moderator '", moderator, "': ", e$message)
    })
  }
  
  if (all_together) {
    combined_moderators <- c()
    for (moderator in moderators) {
      if (!moderator %in% colnames(data)) {
        warning("Moderator '", moderator, "' not found in the data. Skipping this moderator for combined model.")
        next
      }
      
      tryCatch({
        combined_moderators <- c(combined_moderators, moderator)
        combined_formula <- paste(combined_moderators, collapse = " + ")
        combined_model <- robu(formula = as.formula(paste0("hedges_g ~ ", combined_formula)), data = data, 
                               studynum = unique_ID, var.eff.size = vi_g, 
                               rho = rho, modelweights = "HIER", small = FALSE)
        moderator_models[["moderator_all"]] <- combined_model
      }, error = function(e) {
        warning("An error occurred while adding moderator '", moderator, "' to the combined model: ", e$message)
        combined_moderators <- setdiff(combined_moderators, moderator)
      })
    }
  }
  
  if (!list_report) {
    return(moderator_models)
  }
  
  result_list <- list()
  
  for (moderator in names(moderator_models)) {
    model <- moderator_models[[moderator]]
    k <- nrow(model$data)  # Number of effect sizes
    reg_table <- model$reg_table
    
    reference <- references[[moderator]]
    
    # Format the labels: remove moderator name and append (vs reference)
    reg_table <- reg_table %>%
      mutate(
        labels = case_when(
          grepl("^X.Intercept.$", labels) ~ "(Intercept)",  # Format intercept
          !is.null(reference) ~ gsub(paste0("^", moderator), "", labels) %>%
            paste0(" (vs ", reference, ")"),  # Remove moderator name and append reference
          TRUE ~ labels
        )
      )
    
    subset_description <- paste0("Moderator Model- ", gsub("_", " ", moderator))
    
    results_table <- reg_table %>%
      mutate(
        Test = labels, 
        g = round(b.r, 2), 
        SE = round(SE, 2), 
        t = round(t, 2), 
        df = round(dfs, 2), 
        p = format.pval(prob, digits = 3, eps = 0.001, na.form = "<.001"), 
        `95 CI` = paste0("[", round(CI.L, 2), ", ", round(CI.U, 2), "]"), 
        sig = adjust_stars(sig) 
      ) %>%
      select(Test, g, SE, t, df, p, `95 CI`, sig)
    
    # Add n_clusters and n_obs as additional rows
    n_clusters <- model$N
    n_obs <- model$M
    summary_row <- tibble::tibble(
      Test = c("N clusters", "N observations"),
      g = NA, SE = NA, t = NA, df = NA, p = NA, `95 CI` = NA, sig = NA
    )
    summary_row$g <- c(n_clusters, n_obs)
    results_table <- bind_rows(results_table, summary_row)
    
    result_list[[moderator]] <- results_table
    
    # Create LaTeX table using kableExtra
    latex_table <- results_table %>%
      kbl(
        format = "latex",
        booktabs = TRUE,
        align = "lrrrrrrr"
      ) %>%
      kable_styling(
        latex_options = c("hold_position"), 
        full_width = FALSE
      ) %>%
      add_header_above(setNames(8, subset_description))  # Correct header format
    
    # Write the LaTeX table to a .tex file
    tex_filename <- normalizePath(file.path(file_path, paste0("moderator_analysis_", moderator, ".tex")), mustWork = FALSE)
    
    tryCatch({
      cat(latex_table, file = tex_filename)
      if (file.exists(tex_filename)) {
        message("File successfully created: ", tex_filename)
      } else {
        warning("Failed to create file: ", tex_filename)
      }
    }, error = function(e) {
      warning("An error occurred while writing file for moderator '", moderator, "': ", e$message)
    })
  }
  
  return(result_list)
}

```

## 7.2 Preregistered Moderators

```{r}
# Convert 'learning_domain' to a factor if it's not already
data_clean$feedback_type_simple_elaborated <- factor(data_clean$feedback_type_simple_elaborated)

# Relevel the factor to make "text_memory" the reference category
data_clean$feedback_type_simple_elaborated <- relevel(data_clean$feedback_type_simple_elaborated, ref = "simple")
```


### 7.2.a- Overall
no small number adjustments
```{r}
data_clean$educational_level <- factor(data_clean$educational_level)
data_clean$educational_level <- relevel(data_clean$educational_level, ref = "tertiary")
# Define the list of moderators
preregistered_moderators <- c(
  "feedback_type_simple_elaborated", 
  "delay_definition", 
  "feedback_delay_difference_converted_to_time_log",
  "educational_level",  
  "learning_domain", 
  "task_level", 
  "prior_knowledge", 
  "experimental_vs_curriculum_based_task"
)

# Run the function
moderator_models_preregistered <- calculate_moderator_models(input_data = data_clean, 
                                      moderators = preregistered_moderators, 
                                      list_report = TRUE, 
                                      file_path = file_path,
                                      all_together = TRUE,
                                      threshold_for_moderator = threshold_for_moderator, remove_small_groups = TRUE)

moderator_models_preregistered

```

small number adjustment
```{r}
# Define the list of moderators
preregistered_moderators <- c(
  "feedback_type_simple_elaborated", 
  "delay_definition", 
  "feedback_delay_difference_converted_to_time_log",
  "educational_level_tertiary_others",  
  "learning_domain", 
  "task_level", 
  "prior_knowledge", 
  "experimental_vs_curriculum_based_task"
)

# Run the function
moderator_models_preregistered <- calculate_moderator_models(input_data = data_clean, 
                                      moderators = preregistered_moderators, 
                                      list_report = TRUE, 
                                      file_path = file_path,
                                      all_together = TRUE,
                                      threshold_for_moderator = threshold_for_moderator, remove_small_groups = TRUE)

moderator_models_preregistered


```

### 7.2.b- Only in time based delays
```{r}
time_data = subset(data_clean, delay_definition == "seconds")

#Scale?
#time_data$feedback_delay_difference=scale(time_data$feedback_delay_difference)
#time_data$retention_interval_difference_btw_lastfeedback_posttest=scale(time_data$retention_interval_difference_btw_lastfeedback_posttest)

# Define the list of moderators
preregistered_moderators_for_time <- c(
  "feedback_type_simple_elaborated", 
  "feedback_delay_difference",
  "educational_level",  
  "learning_domain", 
  "task_level", 
  "prior_knowledge", 
  "experimental_vs_curriculum_based_task",
  "retention_interval_difference_btw_lastfeedback_posttest",
  "delayed_feedback_given_in",
  "feedback_delay_difference_converted_to_time_log"
)

# Run the function
moderator_models_preregistered_timeonly <- calculate_moderator_models(input_data = time_data, 
                                      moderators = preregistered_moderators_for_time, 
                                      list_report = TRUE, 
                                      file_path = file_path,
                                      all_together = TRUE,
                                      threshold_for_moderator = threshold_for_moderator, remove_small_groups = TRUE)

moderator_models_preregistered_timeonly


```



### 7.2.c- Only in item based delays
```{r}

item_data =  subset(data_clean, delay_definition == "item")

#item_data$feedback_delay_difference=scale(item_data$feedback_delay_difference)
#item_data$feedback_delay_difference_converted=scale(item_data$feedback_delay_difference_converted)

# Define the list of moderators
preregistered_moderators_for_item <- c(
  "feedback_type_simple_elaborated", 
  "feedback_delay_difference",
  "educational_level",  
  "learning_domain", 
  "task_level", 
  "prior_knowledge", 
  "experimental_vs_curriculum_based_task",
  "feedback_delay_difference_converted",
  "feedback_delay_difference_converted_to_time_log"
)

# Run the function
moderator_models_preregistered_itemonly <- calculate_moderator_models(input_data = item_data, 
                                      moderators = preregistered_moderators_for_item, 
                                      list_report = TRUE, 
                                      file_path = file_path,
                                      all_together = TRUE,
                                      threshold_for_moderator = threshold_for_moderator, remove_small_groups = TRUE)

moderator_models_preregistered_itemonly


```
combine them

```{r}
# Create a new list with only the data frames you want
combined_item_time <- list(
  feedback_delay_difference_converted_to_time_log = moderator_models_preregistered_timeonly$feedback_delay_difference_converted_to_time_log,
  feedback_delay_difference = moderator_models_preregistered_itemonly$feedback_delay_difference,
  feedback_delay_difference_converted = moderator_models_preregistered_itemonly$feedback_delay_difference_converted_to_time_log
)

combined_item_time




```


###are they comparable?
```{r}
# Load required libraries
library(ggplot2)
library(broom)  # For tidying model results

# Assuming item_data is your data frame
# Example structure of item_data (replace this with your actual data frame)
# item_data <- read.csv("path/to/your/file.csv")

# Fit a linear model to calculate the statistics
model <- lm(feedback_delay_difference_converted ~ feedback_delay_difference, data = item_data)

# Extract the slope, intercept, p-value, and R-squared
model_stats <- broom::tidy(model)
r_squared <- summary(model)$r.squared
p_value <- model_stats$p.value[2]  # p-value for the slope
slope <- model_stats$estimate[2]   # slope of the regression line
intercept <- model_stats$estimate[1]  # intercept of the regression line

# Format the statistics to display them on the plot
stats_text <- paste0(
  "Slope = ", round(slope, 3), 
  "\nIntercept = ", round(intercept, 3), 
  "\nR² = ", round(r_squared, 3), 
  "\np = ", ifelse(p_value < 0.001, "< 0.001", round(p_value, 3))
)

# Create the scatter plot with regression line and annotated statistics
correlation_item_time=ggplot(item_data, aes(x = feedback_delay_difference, y = feedback_delay_difference_converted)) +
  geom_point(color = "#5E81AC", alpha = 0.6, size = 3) +  # Scatter points
  geom_smooth(method = "lm", color = "#893F45", se = TRUE) +  # Regression line with confidence interval
  labs(
    title = "",
    x = "Feedback Delay Difference (Item)",
    y = "Converted to Seconds"
  ) +
  annotate("text", 
           x = max(item_data$feedback_delay_difference, na.rm = TRUE) * 0.7, 
           y = max(item_data$feedback_delay_difference_converted, na.rm = TRUE) * 0.9, 
           label = stats_text, 
           hjust = 0, vjust = 1, size = 4, color = "black", fontface = "bold") +
plot_theme

correlation_item_time

ggsave("correlation_item_time.png", plot = correlation_item_time, width = 10, height = 8, dpi = 300)


```

## 7.3- Exploratory Moderators

```{r}
# Convert 'learning_domain' to a factor if it's not already
data_clean$time_limit_for_answer_include_not_reported <- factor(data_clean$time_limit_for_answer_include_not_reported)

# Relevel the factor to make "text_memory" the reference category
data_clean$time_limit_for_answer_include_not_reported <- relevel(data_clean$time_limit_for_answer_include_not_reported, ref = "answer_time_not_limited")
```

```{r}
# # Define the list of moderators
# exploratory_moderators <- c("participant_design", "arbitrary_learning","item_posttest", 
#                     "delayed_feedback_given_in", "retention_interval", "feedback_provided", "feedback_remind_answer", "nb_item_in_training", 
#                     "posttest_category", "learning_material_type_in_training","memory_retrieval_vs_knowledge_application", 
#                     "feedback_type_kr_kcr_ef_tryagain", "feedback_type_simple_elaborated","year","time_limit_for_answer", "time_limit_for_answer_include_not_reported",
#                     "feedback_i_d_rate","interval_btw_last_feedback_and_posttest_controlled", "prior_knowledge","feedback_delay_difference_converted_to_time_log", "retention_interval_difference_btw_lastfeedback_posttest"
# )

exploratory_moderators <- c("participant_design", "arbitrary_learning","item_posttest", 
                   "feedback_provided", "feedback_remind_answer", "nb_item_in_training", 
                    "memory_retrieval_vs_knowledge_application", "year", "time_limit_for_answer_include_not_reported",
                    "retention_interval_difference_btw_lastfeedback_posttest"
)

# Run the function
moderator_models_exploratory <- calculate_moderator_models(input_data = data_clean, 
                                      moderators = exploratory_moderators, 
                                      list_report = TRUE, 
                                      file_path = file_path,
                                      all_together = FALSE,
                                      threshold_for_moderator = threshold_for_moderator, remove_small_groups = TRUE)

moderator_models_exploratory



```


## 7.4- Multiple MetaRegression (Only significant Moderators)

### 7.4.a- first regroup the minority categories

##### check learning_domain - whether its meaningful to merge "text_memory", "reading_comprehension"
```{r}
# Convert 'learning_domain' to a factor if it's not already
data_clean$learning_domain <- factor(data_clean$learning_domain)

# Relevel the factor to make "text_memory" the reference category
data_clean$learning_domain <- relevel(data_clean$learning_domain, ref = "text_memory")


moderator_learning_domain  <-  robu(formula = hedges_g ~ learning_domain, data = data_clean,
                     studynum = unique_ID, var.eff.size = vi_g,
                    rho = rho,  modelweights = "HIER", small = FALSE)

moderator_learning_domain

data_clean <- data_clean %>%
  mutate(learning_domain_formetareg = case_when(
    learning_domain %in% c("text_memory", "reading_comprehension") ~ "text_based_learning",
    TRUE ~ "others"  # Groups all other categories into "others"
  ))

# You can check the changes with
unique(data_clean$learning_domain_formetareg)

moderator_learning_domain  <-  robu(formula = hedges_g ~ learning_domain_formetareg, data = data_clean,
                     studynum = unique_ID, var.eff.size = vi_g,
                    rho = rho,  modelweights = "HIER", small = FALSE)

moderator_learning_domain

```

##### check educational level - whether its meaningful to merge "tertiary", "adult_education"
```{r}
# Convert 'learning_domain' to a factor if it's not already
data_clean$educational_level <- factor(data_clean$educational_level)

# Relevel the factor to make "text_memory" the reference category
data_clean$educational_level <- relevel(data_clean$educational_level, ref = "tertiary")


moderator_educational_level  <-  robu(formula = hedges_g ~ educational_level, data = data_clean,
                     studynum = unique_ID, var.eff.size = vi_g,
                    rho = rho,  modelweights = "HIER", small = FALSE)

moderator_educational_level

data_clean <- data_clean %>%
  mutate(educational_level_formetareg = case_when(
      educational_level %in% c("tertiary", "adult_education") ~ "tertiary+adult",
      educational_level %in% c("primary", "secondary") ~ "primary+secondary",
      TRUE ~ "other"  # This will categorize all remaining levels as "other"
  ))

# You can check the changes with
unique(data_clean$educational_level_formetareg)

# Convert 'learning_domain' to a factor if it's not already
data_clean$educational_level_formetareg <- factor(data_clean$educational_level_formetareg)

# Relevel the factor to make "text_memory" the reference category
data_clean$educational_level_formetareg <- relevel(data_clean$educational_level_formetareg, ref = "tertiary+adult")

moderator_educational_level  <-  robu(formula = hedges_g ~ educational_level_formetareg, data = data_clean,
                     studynum = unique_ID, var.eff.size = vi_g,
                    rho = rho,  modelweights = "HIER", small = FALSE)

moderator_educational_level

```

### 7.4.b- run the metareg

```{r}
# Define the list of moderators
#"educational_level_tertiary_others","learning_domain", "memory_retrieval_vs_knowledge_application", "year", "time_limit_for_answer"
significant_moderators <- c("educational_level_formetareg","learning_domain_formetareg", "time_limit_for_answer_include_not_reported"
)

# Run the function
moderator_models_significant_moderators <- calculate_moderator_models(input_data = data_clean, 
                                      moderators = significant_moderators, 
                                      list_report = TRUE, 
                                      file_path = file_path,
                                      all_together = TRUE,
                                      threshold_for_moderator = threshold_for_moderator, remove_small_groups = FALSE)

moderator_models_significant_moderators


```

# 8- Correlation Plot

```{r}
plot_correlations <- function(data, ref_variable, list_correlation_variables) {
  library(ggplot2)
  library(gridExtra)  # For arranging subplots
  library(broom)  # For extracting model stats
  library(robumeta)  # For robust regression models

  plots <- list()  # Initialize an empty list to store plots

  for (var in list_correlation_variables) {
    var_title <- gsub("_", " ", var)
    # Check if the variable is numeric or categorical
    if (is.numeric(data[[var]])) {
      # Fit the linear model for numeric variables
      model <- lm(as.formula(paste(ref_variable, var, sep=" ~ ")), data = data)
      model_stats <- broom::tidy(model)
      r_squared <- summary(model)$r.squared
      p_value <- model_stats$p.value[2]  # Assuming slope is the second coefficient
      slope <- model_stats$estimate[2]   # Slope of the regression line
      intercept <- model_stats$estimate[1]  # Intercept of the regression line

      # Create the scatter plot with regression line (gray theme)
      plot <- ggplot(data, aes_string(x = ref_variable, y = var)) +
        geom_point(color = "gray50", alpha = 0.6, size = 3) +  # Grey scatter points
        geom_smooth(method = "lm", color = "black", se = TRUE) +  # Black regression line
        labs(x = ref_variable, y = gsub("_", " ", var)) +
        theme_minimal() +
        theme(
          axis.title = element_text(size = 12, face = "bold"),
          plot.title = element_text(hjust = 0.5),
          legend.position = "none"
        ) +
        ggtitle(var_title) +  # Add formatted title
        plot_theme +
        theme(legend.position = "none")

    } else {
      # Create the half-violin plot for categorical variables
      plot <- ggplot(data, aes_string(x = var, y = ref_variable, fill = var)) +
        geom_violin(trim = TRUE, scale = "area", adjust = 1, width = 0.8, fill = "gray70") +  # Removed draw_quantiles
        geom_jitter(width = 0.05, color = "#5A75AA", alpha = 0.9, size = 3) +  # Grey jittered points
        coord_flip() +
        labs(x = "", y = gsub("_", " ", ref_variable)) +
        theme_minimal() +
        theme(
          axis.title = element_text(size = 12, face = "bold"),
          plot.title = element_text(hjust = 0.5),
          legend.position = "none"
        ) +
        ggtitle(var_title) +  # Add formatted title
        plot_theme +
        theme(legend.position = "none")
    }

    # Add plot to list
    plots[[var]] <- plot

    # Print robust regression model for each variable
    combined_moderators <- c(ref_variable, var)
    combined_formula <- paste(combined_moderators, collapse = " + ")
    combined_model <- robu(
      formula = as.formula(paste0("hedges_g ~ ", combined_formula)), 
      data = data, 
      studynum = unique_ID, 
      var.eff.size = vi_g, 
      rho = rho, 
      modelweights = "HIER", 
      small = FALSE
    )
    
    print(combined_model)  # Print model output
  }

  # Create subplot arrangement (2 per row)
  num_plots <- length(plots)
  ncol <- 2  # 2 plots per row
  nrow <- ceiling(num_plots / ncol)

  # Arrange plots into one combined plot
  combined_plot <- do.call(grid.arrange, c(plots, ncol = ncol, nrow = nrow))

  # Save the final combined plot
  ggsave("total_correlation.png", combined_plot, width = 20, height = 6 * nrow)

  return(combined_plot)
}

# Create a new dataframe for correlation analysis and rename columns
for_correlation <- data_clean %>%
  select(
    unique_ID, 
    hedges_g, 
    vi_g, 
    year, 
    educational_level_formetareg, 
    learning_domain_formetareg, 
    time_limit_for_answer_include_not_reported
  ) %>%
  rename(
    publication_year = year,
    educational_level = educational_level_formetareg,
    learning_domain = learning_domain_formetareg,
    time_limitation_for_responses = time_limit_for_answer_include_not_reported
  )

# Function to replace underscores with spaces in all character columns
replace_underscore <- function(df) {
  df %>%
    mutate(across(where(is.character), ~ gsub("_", " ", .)))
}

# Apply the function to rename values
for_correlation <- replace_underscore(for_correlation)

# Define the significant categorical moderators with spaces instead of underscores
significant_moderators <- c("educational_level", 
                            "learning_domain", 
                            "time_limitation_for_responses")

# Update reference variable name to match the renamed column
ref_variable <- "publication_year"

# Call the function using the for_correlation dataset
correlation_plots <- plot_correlations(for_correlation, ref_variable, list_correlation_variables = significant_moderators)

# Print the plots
if (!is.null(correlation_plots)) {
  for (plot_name in names(correlation_plots)) {
    print(correlation_plots[[plot_name]])
  }
}
```

# 9- statistics of immediate and delayed delays

```{r}

# Filter time-based data
time_data <- subset(data_clean, delay_definition == "seconds")

# Compute statistics
summary_time <- time_data %>%
  summarise(
    mean_i = mean(delay_i.seconds.item., na.rm = TRUE),
    sd_i = sd(delay_i.seconds.item., na.rm = TRUE),
    median_i = median(delay_i.seconds.item., na.rm = TRUE),
    min_i = min(delay_i.seconds.item., na.rm = TRUE),
    max_i = max(delay_i.seconds.item., na.rm = TRUE),
    
    mean_d = mean(delay_d.seconds.item., na.rm = TRUE),
    sd_d = sd(delay_d.seconds.item., na.rm = TRUE),
    median_d = median(delay_d.seconds.item., na.rm = TRUE),
    min_d = min(delay_d.seconds.item., na.rm = TRUE),
    max_d = max(delay_d.seconds.item., na.rm = TRUE)
  )

# Generate formatted text
cat(sprintf(
  "Among studies that defined delay in seconds (time-based), the mean delay for immediate feedback was %.2f seconds (SD = %.2f, median = %.2f, range = %.2f–%.2f), and for delayed feedback it was %.2f seconds (SD = %.2f, median = %.2f, range = %.2f–%.2f).",
  summary_time$mean_i, summary_time$sd_i, summary_time$median_i, summary_time$min_i, summary_time$max_i,
  summary_time$mean_d, summary_time$sd_d, summary_time$median_d, summary_time$min_d, summary_time$max_d
))

geo_mean <- function(x) {
  exp(mean(log(x[x > 0]), na.rm = TRUE))  # avoid zeros
}


summary_time <- time_data %>%
  summarise(
    mean_i = mean(delay_i.seconds.item., na.rm = TRUE),
    sd_i = sd(delay_i.seconds.item., na.rm = TRUE),
    median_i = median(delay_i.seconds.item., na.rm = TRUE),
    min_i = min(delay_i.seconds.item., na.rm = TRUE),
    max_i = max(delay_i.seconds.item., na.rm = TRUE),
    
    geo_mean_d = geo_mean(delay_d.seconds.item.),
    sd_d = sd(delay_d.seconds.item., na.rm = TRUE),
    median_d = median(delay_d.seconds.item., na.rm = TRUE),
    min_d = min(delay_d.seconds.item., na.rm = TRUE),
    max_d = max(delay_d.seconds.item., na.rm = TRUE)
  )

# Generate formatted text
cat(sprintf(
  "Among studies that defined delay in seconds (time-based), the mean delay for immediate feedback was %.2f seconds (SD = %.2f, median = %.2f, range = %.2f–%.2f), and for delayed feedback it was approximately %.2f seconds (geometric mean, SD = %.2f, median = %.2f, range = %.2f–%.2f).",
  summary_time$mean_i, summary_time$sd_i, summary_time$median_i, summary_time$min_i, summary_time$max_i,
  summary_time$geo_mean_d, summary_time$sd_d, summary_time$median_d, summary_time$min_d, summary_time$max_d
))


# Filter item-based data
item_data <- subset(data_clean, delay_definition == "item")

# Compute statistics
summary_item <- item_data %>%
  summarise(
    mean_i = mean(delay_i.seconds.item., na.rm = TRUE),
    sd_i = sd(delay_i.seconds.item., na.rm = TRUE),
    median_i = median(delay_i.seconds.item., na.rm = TRUE),
    min_i = min(delay_i.seconds.item., na.rm = TRUE),
    max_i = max(delay_i.seconds.item., na.rm = TRUE),
    
    mean_d = mean(delay_d.seconds.item., na.rm = TRUE),
    sd_d = sd(delay_d.seconds.item., na.rm = TRUE),
    median_d = median(delay_d.seconds.item., na.rm = TRUE),
    min_d = min(delay_d.seconds.item., na.rm = TRUE),
    max_d = max(delay_d.seconds.item., na.rm = TRUE)
  )

# Generate formatted text
cat(sprintf(
  "Among studies that defined delay in terms of item count, the mean delay for immediate feedback was %.2f items (SD = %.2f, median = %.2f, range = %.2f–%.2f), and for delayed feedback it was %.2f items (SD = %.2f, median = %.2f, range = %.2f–%.2f).",
  summary_item$mean_i, summary_item$sd_i, summary_item$median_i, summary_item$min_i, summary_item$max_i,
  summary_item$mean_d, summary_item$sd_d, summary_item$median_d, summary_item$min_d, summary_item$max_d
))



```

